---
title: "Null distributions for $\\delta$"
author: "D. Erik Boonstra, MS"
output:
  html_document:
    toc: TRUE
    toc_depth: 4
    toc_float: TRUE
---

```{r, include = FALSE, results = FALSE, message = FALSE}
R <- list.files(path = "./R", pattern = "*.R", full.names = TRUE)
sapply(R, source, .GlobalEnv)
knitr::opts_chunk$set(
  echo = FALSE,
  out.width = "100%",
  fig.align = "center",
  warning = FALSE
)
```

# Purpose
Explore the null distrubtion of the $\delta$ statistic. The null distribution will be characterized by the $\delta$ values produced by the working correlation structures that are also the generating correlation structures.

# Definition of $\delta$
Given two square matrices, $\mathbf{A}$ and $\mathbf{B}$, of the same dimension, $d$, let $\delta$ be define as the following:
$$
\delta(\mathbf{A}, \mathbf{B}) = \sum_{i = 1}^{d} max\left(\frac{b_{ii}}{a_{ii}}, \frac{a_{ii}}{b_{ii}}\right),
$$

where $a_{ii}$ and $b_{ii}$ are the diagonal elements of the matrices $\mathbf{A}$ and $\mathbf{B}$. The minimum value for $\delta$ will be the dimension of the matrices $d$. This minimum will be achieved if $a_{ii} \approx b_{ii}$ for all $i$. By the definition of $\delta$, this measure is a symmetric discrepancy.

## $\delta$ for GEEs
Let $R(\alpha) = R$ be the working correlation structure and $\hat{\boldsymbol{\beta}}(R)$ be mean parameter estimator given $R$. Furthermore, let the model-based estimated covariance matrix of $\hat{\boldsymbol{\beta}}$ be $\hat{\boldsymbol{\Sigma}}$ and the robust or sandwich estimated covariance matrix of $\hat{\boldsymbol{\beta}}$ be $\hat{\mathbf{V}}_{r}$. Then, in the generalized estimating equations (GEEs) setting, we hope $\delta$ will be able to select the proper correlation structure by comparing the model-based covariance matrix, $\hat{\boldsymbol{\Sigma}}$, given $\hat{\boldsymbol{\beta}}(R)$ to the robust covariance matrix, $\hat{\mathbf{V}}_{r}$, given $\hat{\boldsymbol{\beta}}(R)$. 

$$
\delta = \delta\left(\hat{\boldsymbol{\Sigma}}, \hat{\mathbf{V}}_{r}\right)
$$

The robust covariance matrix $\hat{\mathbf{V}}_{r}$ protects against misspecification of the working correlation structure while the variance estimates for the model-based covariance matrix $\hat{\boldsymbol{\Sigma}}$ could vary drastically based on the working correlation structure. If $\delta \approx k$, where $k$ is the dimension of the parameter vector $\boldsymbol{\beta}$, then one would be able to assume that $\boldsymbol{\Sigma} \approx \mathbf{V}_{r}$ and the working correlation structure is appropriate given the mean structure is specified properly. The use of $\delta$ in the GEEs setting is reasonable because the mean structure estimates are protected against misspecification of the correlation structure and proper selection of correlation structure provides gains in efficiency not accuracy of statistical inference.

# Presentation of results

## Import results
The null distribution parameters are stored in:
```{r, echo = TRUE}
# Null distribution parameters ####
null_dist <- readRDS(
  file = paste0(
    "./outputs/corstr/norm-delta-sim/",
    "norm-delta-null-dist/norm_delta_null_dist.rds"
  )
)
```
while the realized values from the simulations are store in:
```{r, echo = TRUE}
# Realized values ####
realized <- readRDS(
  file = paste0(
    "./outputs/corstr/norm-delta-sim/",
    "norm-delta-null-dist/norm_delta_realized_values.rds"
  )
)
```

and are dependent on the data generation mechanism (`corstr`) plus the simulation setting defined by the number of non-zero mean parameters and the correlation coefficient (`simulation`).

```{r, include = FALSE}
# indices for all N and n values
fixed_n <- 1:7
fixed_obs <- c(8:9, 3, 10:14)
N <- c(rep(200, 7), 300, 240, 150, 120, 100, 80, 75)
n <- c(4, 5, 6, 7, 8, 9, 10, 4, 5, 8, 10, 12, 15, 16)
set.seed(1997)
```

```{r}
# Cleaning up names of corstr
null_dist$corstr <- ifelse(
  test = null_dist$corstr == "exchangeable",
  yes = "Exchangeable",
  no = "AR(1)"
)
realized$corstr <- ifelse(
  test = realized$corstr == "exchangeable",
  yes = "Exchangeable",
  no = "AR(1)"
)
```

```{r}
# Creating a function to plot ####
plot_all <- function(null, realized, dim_beta, alpha, index, corstr) {
  group_id <- paste0("N = ", N[index], ", n = ", n[index])
  nd <- null
  nd$group <- paste0("N = ", nd$N, ", n = ", nd$n)
  nd <- nd[
    (
      nd$dim_beta == dim_beta &
        nd$alpha == alpha &
        nd$group %in% group_id &
        nd$corstr == corstr
    ),
  ]
  res <- realized
  res$group <- paste0("N = ", res$N, ", n = ", res$n)
  res <- res[
    (
      res$dim_beta == dim_beta &
        res$alpha == alpha &
        res$group %in% group_id &
        res$corstr == corstr
    ),
  ]
  nd_vals <- vector(mode = "list", length = length(group_id))
  for (j in seq_along(group_id)) {
    pars <- subset(
      x = nd, subset = group == group_id[j], select = c(shape, rate)
    )
    vals <- rgamma(
      n = 1000, shape = pars$shape, rate = pars$rate
    )
    nd_vals[[j]] <- data.frame(
      group = rep(group_id[j], 1000),
      type = rep("Null", 1000),
      delta = vals
    )
  }
  nd_vals <- dplyr::bind_rows(nd_vals)
  res$type <- "Realized"
  res <- subset(
    x = res,
    select = c(group, type, delta)
  )
  plot_data <- dplyr::bind_rows(nd_vals, res)
  plot_data$group <- factor(
    x = plot_data$group,
    levels = group_id,
    ordered = TRUE
  )
  ggplot2::ggplot(
    data = plot_data,
    mapping = ggplot2::aes(x = delta, fill = type)
  ) +
  ggplot2::geom_density(alpha = 0.5, color = NA) +
  ggplot2::facet_wrap(ggplot2::vars(group), ncol = 2, scales = "free_y") +
  ggplot2::labs(
      x = expression(delta),
      y = "Density"
    ) +
    ggplot2::guides(fill = ggplot2::guide_legend(title = "Type of values")) +
    ggplot2::theme_bw()
}
```

```{r}
# Creating functions to generate tables ####

## Null information ####
null_tab <- function(data, dim_beta, alpha, index, corstr) {
  nd <- data
  nd$group <- paste0("N = ", nd$N, ", n = ", nd$n)
  group_id <- paste0("N = ", N[index], ", n = ", n[index])
  nd <- nd[
    (
      nd$dim_beta == dim_beta &
        nd$alpha == alpha &
        nd$group %in% group_id &
        nd$corstr == corstr
    ),
    !(colnames(nd) %in% c("simulation", "group"))
  ]
  nd <- nd[order(nd$n), ]
  row.names(nd) <- NULL

  nd_tab <- knitr::kable(
    x = nd,
    format = "html",
    digits = 4,
    col.names = c(
      "$dim(\\boldsymbol{\\delta})$", "$\\alpha$",
      "N", "n",
      "Correlation structure",
      "Shape", "Rate", "Scale (1 / Rate)",
      "$\\mathbb{E}(\\delta)$", "$Var(\\delta)$"
    ),
    caption = paste0(
      "Null distributional information for $\\delta$ assuming",
      " $\\delta \\sim \\Gamma(Shape, Rate)$"
    )
  )
  kableExtra::kable_styling(kable_input = nd_tab, full_width = FALSE)
}

## Realized ####
realized_tab <- function(data, dim_beta, alpha, index, corstr) {
  res <- data
  res$group <- paste0("N = ", res$N, ", n = ", res$n)
  group_id <- paste0("N = ", N[index], ", n = ", n[index])
  res <- res[
    (
      res$dim_beta == dim_beta &
        res$alpha == alpha &
        res$group %in% group_id &
        res$corstr == corstr
    ),
    !(colnames(res) %in% c("simulation", "group"))
  ]
  res_tab <- stats::aggregate(
    x = delta ~ dim_beta + alpha + N + n + corstr,
    data = res,
    FUN = function(x) {
      out <- c(mean(x), stats::var(x))
      names(out) <- c("mean", "var")
      return(out)
    }
  )
  res_tab$mean <- res_tab$delta[, "mean"]
  res_tab$var <- res_tab$delta[, "var"]
  res_tab <- subset(x = res_tab, select = colnames(res_tab) != "delta")
  res_tab <- res_tab[order(res_tab$n), ]
  row.names(res_tab) <- NULL
  res_tab <- knitr::kable(
    x = res_tab,
    format = "html",
    digits = 4,
    col.names = c(
      "$dim(\\boldsymbol{\\delta})$", "$\\alpha$",
      "N", "n",
      "Correlation structure",
      "$\\bar{\\delta}$", "$\\widehat{Var}(\\delta)$"
    ),
    caption = paste0(
      "Mean and variance of the realized $\\delta$ values"
    )
  )
  kableExtra::kable_styling(kable_input = res_tab, full_width = FALSE)
}
```

## Examining the distributions of $\delta$
In the results below, the null and realized densities of $\delta$ are plotted with each other along with two tables characterizing the distributions.

### Correlation structure: Exchangeable
The distributions of the $\delta$ presented below are based on the data generation process that used an *exchangeable* correlation structure.

#### $dim(\boldsymbol{\beta}) = 3, \alpha = 0.5$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 3$, which means the $min(\delta) = 4$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.5$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_n,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_n,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_n,
  corstr = "Exchangeable"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "Exchangeable"
)
```

#### $dim(\boldsymbol{\beta}) = 3, \alpha = 0.05$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 3$, which means the $min(\delta) = 4$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.05$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_n,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_n,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_n,
  corstr = "Exchangeable"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "Exchangeable"
)
```

#### $dim(\boldsymbol{\beta}) = 3, \alpha = 0.70$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 3$, which means the $min(\delta) = 4$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.7$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_n,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_n,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_n,
  corstr = "Exchangeable"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "Exchangeable"
)
```

#### $dim(\boldsymbol{\beta}) = 5, \alpha = 0.5$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 5$, which means the $min(\delta) = 6$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.5$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_n,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_n,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_n,
  corstr = "Exchangeable"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "Exchangeable"
)
```

#### $dim(\boldsymbol{\beta}) = 5, \alpha = 0.05$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 5$, which means the $min(\delta) = 6$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.05$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_n,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_n,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_n,
  corstr = "Exchangeable"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "Exchangeable"
)
```

#### $dim(\boldsymbol{\beta}) = 5, \alpha = 0.7$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 5$, which means the $min(\delta) = 6$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.7$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_n,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_n,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_n,
  corstr = "Exchangeable"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "Exchangeable"
)
```

### Correlation structure: AR(1)
The distributions of the $\delta$ presented below are based on the data generation process that used an *AR(1)* correlation structure.

#### $dim(\boldsymbol{\beta}) = 3, \alpha = 0.5$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 3$, which means the $min(\delta) = 4$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.5$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_n,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_n,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_n,
  corstr = "AR(1)"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "AR(1)"
)
```

#### $dim(\boldsymbol{\beta}) = 3, \alpha = 0.05$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 3$, which means the $min(\delta) = 4$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.05$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_n,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_n,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_n,
  corstr = "AR(1)"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "AR(1)"
)
```

#### $dim(\boldsymbol{\beta}) = 3, \alpha = 0.70$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 3$, which means the $min(\delta) = 4$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.7$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_n,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_n,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_n,
  corstr = "AR(1)"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "AR(1)"
)
```

#### $dim(\boldsymbol{\beta}) = 5, \alpha = 0.5$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 5$, which means the $min(\delta) = 6$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.5$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_n,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_n,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_n,
  corstr = "AR(1)"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "AR(1)"
)
```

#### $dim(\boldsymbol{\beta}) = 5, \alpha = 0.05$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 5$, which means the $min(\delta) = 6$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.05$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_n,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_n,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_n,
  corstr = "AR(1)"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "AR(1)"
)
```

#### $dim(\boldsymbol{\beta}) = 5, \alpha = 0.7$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 5$, which means the $min(\delta) = 6$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.7$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_n,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_n,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_n,
  corstr = "AR(1)"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "AR(1)"
)
```