---
title: "Simulations investigating the correlation structure selection properties for Kullback directed divergence"
author: "D. Erik Boonstra, MS"
output:
  html_document:
    toc: TRUE
    toc_depth: 2
    toc_float: TRUE
---

```{r, include = FALSE, results = FALSE, message = FALSE}
R <- list.files(path = "./R", pattern = "*.R", full.names = TRUE)
sapply(R, source, .GlobalEnv)
knitr::opts_chunk$set(
  echo = FALSE,
  out.width = "100%",
  fig.align = "center",
  warning = FALSE
)
```

# Purpose of simulations
The results of these simulations are to investigate the correlation structure selection properties of the Kullback directed divergence (KDD). 

# Definition of KDD
The functional form of KDD in the generalized estimating equations setting is based on the asymptotic distribution of $\hat{\boldsymbol{\beta}},$ 

$$K^{1/2}\left(\hat{\boldsymbol{\beta}} - \boldsymbol{\beta}\right) \sim N\left(\mathbf{0}, \hat{\mathbf{V}}_{r}\right),$$ 

where $K$ is number of parameters in $\boldsymbol{\beta}$ and $\mathbf{V}_{r}$ is the robust covariance matrix of $\hat{\boldsymbol{\beta}}$. Then, the KDD becomes

$$
KDD = \frac{1}{2}\left(\log\frac{|\boldsymbol{\Sigma}_{MB}|}{|\mathbf{V}_{r}|} + tr\left(\boldsymbol{\Sigma}_{MB}^{-1}\mathbf{V}_{r}\right) + (\boldsymbol{\mu_{2}} - \boldsymbol{\mu}_{1})^{\top}\boldsymbol{\Sigma}_{MB}^{-1}(\boldsymbol{\mu_{2}} - \boldsymbol{\mu}_{1}) - K\right), \\
$$

where $\boldsymbol{\Sigma}_{MB}$ is the model-based covariance matrix for $\hat{\boldsymbol{\beta}}$. Considering $\hat{\boldsymbol{\beta}}$ consistent regardless of the working correlation structure,

$$
KDD = \frac{1}{2}\left(\log\frac{|\boldsymbol{\Sigma}_{MB}|}{|\mathbf{V}_{r}|} + tr\left(\boldsymbol{\Sigma}_{MB}^{-1}\mathbf{V}_{r}\right) - K\right), \\
$$

In these simulations, we will be assuming that $\boldsymbol{\Sigma}_{MB} = \boldsymbol{\Sigma}_{MB(R)},$ where $\boldsymbol{\Sigma}_{MB(R)}$ is the model-based working covariance matrix based on the working correlation structure of interest.

# Simulation setup

## Data
```{r, include = FALSE}
nsims <- 1000L
beta <- c(2.0, 3.0, 0.5, 0, 0, 0)
w <- which(beta != 0)
l <- length(w)
N <- c(rep(200, 7), 300, 240, 150, 120, 100, 80, 75)
n <- c(4, 5, 6, 7, 8, 9, 10, 4, 5, 8, 10, 12, 15, 16)
names_work_corstr <- c(
  "independence",
  "exchangeable",
  "ar1",
  "ar3",
  "unstructured"
)
mv <- c(1, 1, 1, 3, 1)
legend_work_corstr <- paste0(
  toupper(substr(names_work_corstr, 1, 1)),
  substr(names_work_corstr, 2, nchar(names_work_corstr))
)
legend_work_corstr <- ifelse(
  test = legend_work_corstr == "Ar1",
  yes = "AR(1)",
  no = legend_work_corstr
)
legend_work_corstr <- ifelse(
  test = legend_work_corstr == "Ar3",
  yes = "AR(3)",
  no = legend_work_corstr
)
```

Following Wang *et al.* (2012) with one-thousand replications, the correlated normal responses are generated from the model $$y_{ij} = \mathbf{X}_{ij}^{\top}\boldsymbol{\beta} + \varepsilon_{ij},$$ where $i = 1, \ldots, N,$ $j = 1, \ldots, n,$ $\mathbf{X}_{ij} = (x_{ij, 1}, \ldots, x_{ij, 6})^{\top},$ and $\boldsymbol{\beta} = (2.0, 3.0, 0.5, 0.0, 0.0, 0.0)^{\top}$, where the combinations of $N$ and $n$ are listed below.

```{r, echo = FALSE}
all_combos <- data.frame(N = N, n = n)
tab <- knitr::kable(
  x = all_combos,
  format = "html",
  col.names = c("$N$", "$n$")
)
kableExtra::kable_styling(
  kable_input = tab,
  full_width = FALSE
)
```

- For the covariates,
    - $x_{ij,1}$ was generated from the Bernoulli(0.5) distribution, and 
    - each $x_{ij,k}$ for $k = 2, \ldots, 6$ was generated from the multivariate normal distribution with mean 0 and an AR(1) covariance matrix with marginal variance 1 and auto-correlation coefficient 0.5.
- The random errors $(\varepsilon_{i1}, \ldots, \varepsilon_{in})^{\top}$ are generated from the multivariate normal distribution with marginal mean 0, marginal variance 1, and either an **exchangeable** or **AR(1)** correlation structure with a correlation parameter of $\alpha = 0.5$.

## Fitting procedure
Considering the focus of these simulations are on the correlation structure selection, each model, based on data generated by an **exchangeable** or **AR(1)** correlation structure, was fitted using generalized estimating equations. The mean structure was properly specified as $\mathbf{X}_{1}$, $\mathbf{X}_{2}$, and $\mathbf{X}_{3}$ with an intercept that was estimated to be approximately 0. To assess the correlation structure selection properties, the working correlation structure was specified as:

- independence,
- exchangeable,
- AR(1),
- AR(3), and
- unstructured.

## Model selection process
In these simulations, there are four sets of comparisons being made between the four correlation structures. These comparisons are:

1. exchangeable versus AR(1),
2. exchangeable versus AR(1) versus independence,
3. exchangeable versus AR(1) versus independence versus AR(3), and
4. exchangeable versus AR(1) versus independence versus AR(3) versus unstructured.

We are making these comparisons because previous research usually only focuses on exchangeable and AR(1). As these simulations are meant to investigate the selection properties of KDD, for each comparison, the correlation structure that resulted in the minimum KDD value was selected as the best performing correlation structure.

# Presentation of results

## Import results
The simulation results are stored in:
```{r, echo = TRUE}
sub_dir <- "./outputs/corstr/norm-kdd-sim/norm-kd-directed-sim/"
res <- readRDS(
  file = paste0(sub_dir, "norm_kd_directed_sim.rds")
)
```

```{r, include = FALSE}
# indices for all N and n values
fixed_n <- 1:7
fixed_obs <- c(8:9, 3, 10:14)
```

```{r, include = FALSE}
# creating a function to plot histograms
plot_all <- function(data, index, min_val) {
  # Subsetting the results to only include the results of focus based on index
  res_plot <- data
  res_plot$group <- paste0("N = ", res_plot$N, ", n = ", res_plot$n)
  group_id <- paste0("N = ", N[index], ", n = ", n[index])
  res_plot <- subset(x = res_plot, subset = res_plot$group %in% group_id)
  res_plot$group <- factor(
    x = res_plot$group,
    levels = group_id,
    ordered = TRUE
  )

  # plotting kdd values

  ## Independence
  independence_plot <- ggplot2::ggplot(
    data = res_plot,
    mapping = ggplot2::aes(x = independence, fill = group)
  ) +
    ggplot2::geom_density(alpha = 0.5, color = NA) +
    ggplot2::geom_vline(
      xintercept = min_val, linetype = "dotted", color = "firebrick",
      linewidth = 1
    ) +
    ggplot2::labs(
      x = "KDD",
      y = "Density",
      title = "Working correlation: Independence"
    ) +
    ggplot2::guides(fill = ggplot2::guide_legend(title = "N =, n =")) +
    ggplot2::theme_bw() +
    ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5, size = 10))

  ## Exchangeable
  exchangeable_plot <- ggplot2::ggplot(
    data = res_plot,
    mapping = ggplot2::aes(x = exchangeable, fill = group)
  ) +
    ggplot2::geom_density(alpha = 0.5, color = NA) +
    ggplot2::geom_vline(
      xintercept = min_val, linetype = "dotted", color = "firebrick",
      linewidth = 1
    ) +
    ggplot2::labs(
      x = "KDD",
      y = "Density",
      title = "Working correlation: Exchangeable"
    ) +
    ggplot2::guides(fill = ggplot2::guide_legend(title = "N =, n =")) +
    ggplot2::theme_bw() +
    ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5, size = 10))

  ## AR(1)
  ar1_plot <- ggplot2::ggplot(
    data = res_plot,
    mapping = ggplot2::aes(x = ar1, fill = group)
  ) +
    ggplot2::geom_density(alpha = 0.5, color = NA) +
    ggplot2::geom_vline(
      xintercept = min_val, linetype = "dotted", color = "firebrick",
      linewidth = 1
    ) +
    ggplot2::labs(
      x = "KDD",
      y = "Density",
      title = "Working correlation: AR(1)"
    ) +
    ggplot2::guides(fill = ggplot2::guide_legend(title = "N =, n =")) +
    ggplot2::theme_bw() +
    ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5, size = 10))

  ## AR(3)
  ar3_plot <- ggplot2::ggplot(
    data = res_plot,
    mapping = ggplot2::aes(x = ar3, fill = group)
  ) +
    ggplot2::geom_density(alpha = 0.5, color = NA) +
    ggplot2::geom_vline(
      xintercept = min_val, linetype = "dotted", color = "firebrick",
      linewidth = 1
    ) +
    ggplot2::labs(
      x = "KDD",
      y = "Density",
      title = "Working correlation: AR(3)"
    ) +
    ggplot2::guides(fill = ggplot2::guide_legend(title = "N =, n =")) +
    ggplot2::theme_bw() +
    ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5, size = 10))

  ## Unstructured
  unstructured_plot <- ggplot2::ggplot(
    data = res_plot,
    mapping = ggplot2::aes(x = unstructured, fill = group)
  ) +
    ggplot2::geom_density(alpha = 0.5, color = NA) +
    ggplot2::geom_vline(
      xintercept = min_val, linetype = "dotted", color = "firebrick",
      linewidth = 1
    ) +
    ggplot2::labs(
      x = "KDD",
      y = "Density",
      title = "Working correlation: Unstructured"
    ) +
    ggplot2::guides(fill = ggplot2::guide_legend(title = "N =, n =")) +
    ggplot2::theme_bw() +
    ggplot2::theme(plot.title = ggplot2::element_text(hjust = 0.5, size = 10))
  ggpubr::ggarrange(
    independence_plot, exchangeable_plot, ar1_plot, ar3_plot,
    unstructured_plot,
    ncol = 2, nrow = 3, common.legend = TRUE, legend = "right"
  )
}
```

```{r, include = FALSE}
# creating functions to calculate statistics

## mean
mean_all <- function(data, index) {
  # Subsetting the results to only include the results of focus based on index
  res_plot <- data
  res_plot$group <- paste0("N = ", res_plot$N, ", n = ", res_plot$n)
  group_id <- paste0("N = ", N[index], ", n = ", n[index])
  res_plot <- subset(x = res_plot, subset = res_plot$group %in% group_id)
  res_plot$group <- factor(
    x = res_plot$group,
    levels = group_id,
    ordered = TRUE
  )
  # Creating table
  mean_tab <- dplyr::group_by(.data = res_plot, group)
  mean_tab <- dplyr::summarise(
    .data = mean_tab,
    independence = mean(independence),
    exchangeable = mean(exchangeable),
    ar1 = mean(ar1),
    ar3 = mean(ar3),
    unstructured = mean(unstructured),
    kb0 = mean(kb0)
  )
  mean_tab <- knitr::kable(
    x = mean_tab, format = "html", digits = 4,
    col.names = c("N =, n =", legend_work_corstr, "$KDD_{0}$"),
    caption = "Mean of values"
  )
  kableExtra::kable_styling(kable_input = mean_tab, full_width = FALSE)
}

## variance
variance_all <- function(data, index) {
  # Subsetting the results to only include the results of focus based on index
  res_plot <- data
  res_plot$group <- paste0("N = ", res_plot$N, ", n = ", res_plot$n)
  group_id <- paste0("N = ", N[index], ", n = ", n[index])
  res_plot <- subset(x = res_plot, subset = res_plot$group %in% group_id)
  res_plot$group <- factor(
    x = res_plot$group,
    levels = group_id,
    ordered = TRUE
  )
  # Creating table
  var_tab <- dplyr::group_by(.data = res_plot, group)
  var_tab <- dplyr::summarise(
    .data = var_tab,
    independence = stats::var(independence),
    exchangeable = stats::var(exchangeable),
    ar1 = stats::var(ar1),
    ar3 = stats::var(ar3),
    unstructured = stats::var(unstructured),
    kb0 = stats::var(kb0)
  )
  var_tab <- knitr::kable(
    x = var_tab, format = "html", digits = 4,
    col.names = c("N =, n =", legend_work_corstr, "$KDD_{0}$"),
    caption = "Variance of values"
  )
  kableExtra::kable_styling(kable_input = var_tab, full_width = FALSE)
}
```

and are dependent on the data generation mechanism (`corstr`).

## Distribution of KDD {.tabset .tabset-fade}
The first set of results being presented are the values of KDD for each working correlation structure across the one-thousand replications given the data generation mechanism. The results are presented based on the data simulation process (i.e., *Fixed N* or *Fixed total number of observations*).

The averages and variances of the oracle values of $KDD$, $KDD_{0}$ is presented along side the averages and variances of statistics. The $KDD_{0}$ is defined as

$$
KDD_{0} = \frac{1}{2}\left(\log\frac{|\boldsymbol{\Sigma}_{MB}|}{|\boldsymbol{\Sigma}_{0}|} + tr\left(\boldsymbol{\Sigma}_{MB}^{-1}\boldsymbol{\Sigma}_{0}\right) - K\right), \\
$$

where $\boldsymbol{\Sigma}_{0}$ is the estimated true covariance matrix.

### Generating correlation structure: Exchangeable
The distributions of the KDD presented below are based on the data generation process that used an *exchangeable* correlation structure.
```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
# Subsetting the results to only include generating correlation structure
res_kdd <- subset(
  x = res,
  subset = corstr == "exchangeable"
)
```

#### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
# plotting kdd values
plot_all(data = res_kdd, index = fixed_n, min_val = 0)

# table summarizing kdd values
## Mean
mean_all(data = res_kdd, index = fixed_n)

## Variance
variance_all(data = res_kdd, index = fixed_n)
```


#### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
# plotting kdd values
plot_all(data = res_kdd, index = fixed_obs, min_val = 0)

# table summarizing kdd values
## Mean
mean_all(data = res_kdd, index = fixed_obs)

## Variance
variance_all(data = res_kdd, index = fixed_obs)
```


### Generating correlation structure: AR(1)
The distributions of the KDD presented below are based on the data generation process that used an *AR(1)* correlation structure.
```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
# Subsetting the results to only include generating correlation structure
res_kdd <- subset(
  x = res,
  subset = corstr == "ar1"
)
```

#### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
# plotting kdd values
plot_all(data = res_kdd, index = fixed_n, min_val = 0)

# table summarizing kdd values
## Mean
mean_all(data = res_kdd, index = fixed_n)

## Variance
variance_all(data = res_kdd, index = fixed_n)
```


#### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
# plotting kdd values
plot_all(data = res_kdd, index = fixed_obs, min_val = 0)

# table summarizing kdd values
## Mean
mean_all(data = res_kdd, index = fixed_obs)

## Variance
variance_all(data = res_kdd, index = fixed_obs)
```

## Correlation structure selection {.tabset .tabset-fade}
Now we will examine the selection properties of KDD given the generating correlation structure and working correlation structures being compared. The comparisons are:

1. exchangeable versus AR(1),
2. exchangeable versus AR(1) versus independence, and
3. exchangeable versus AR(1) versus independence versus AR(3), and
4. exchangeable versus AR(1) versus independence versus AR(3) versus unstructured.

and the results are presented based on the defined numbering system of these comparisons. For each comparison, the hope is the working correlation structure selected by the minimum KDD value is the generating correlation structure the majority of the time.
```{r, echo = FALSE}
corstr_count <- function(x) {
  count_indp <- 0
  count_cs <- 0
  count_ar1 <- 0
  count_ar3 <- 0
  count_un <- 0
  for (i in seq_along(x)) {
    count_indp <- count_indp + (x[i] == "independence")
    count_cs <- count_cs + (x[i] == "exchangeable")
    count_ar1 <- count_ar1 + (x[i] == "ar1")
    count_ar3 <- count_ar3 + (x[i] == "ar3")
    count_un <- count_un + (x[i] == "unstructured")
  }
  temp <- data.frame(
    independence = count_indp, exchangeable = count_cs,
    ar1 = count_ar1, ar3 = count_ar3, un = count_un
  )
  return(temp)
}
```

### Generating correlation structure: Exchangeable {.tabset .tabset-fade .tabset-pills}
The selection properties of the KDD presented below are based on the data generation process that used an *exchangeable* correlation structure.

```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
# Subsetting the results to only include generating correlation structure
# and covariance estimator of interest
res_kdd <- subset(
  x = res,
  subset = corstr == "exchangeable"
)
```

#### Comparison 1

For structure selection comparison 1, we are only considering the working correlation structures of *exchangeable* and *AR(1)*.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
# Subsetting the results to only include the results focused on fixed N
# simulations
res_sel <- res_kdd
res_sel$group <- paste0("N = ", res_sel$N, ", n = ", res_sel$n)
group_id <- paste0("N = ", N[fixed_n], ", n = ", n[fixed_n])
res_sel <- subset(x = res_sel, subset = group %in% group_id)
res_sel$group <- factor(x = res_sel$group, levels = group_id, ordered = TRUE)
res_sel <- res_sel[order(res_sel$group), ]
res_sel <- split(x = res_sel, f = res_sel$group)
sel <- lapply(
  X = res_sel,
  FUN = function(x) {
    data.frame(
      n = unique(x$group),
      corstr_count(x$sel1)
    )
  }
)
sel <- dplyr::bind_rows(sel)
sel_tab <- knitr::kable(
  x = sel, format = "html",
  col.names = c("N = 200, n =", legend_work_corstr),
  caption = "Selection properties for Fixed N"
)
kableExtra::kable_styling(kable_input = sel_tab, full_width = FALSE)
```


##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r, echo = FALSE, fig.align = "center", out.width = "100%", warning = FALSE}
# Subsetting the results to only include the results focused on fixed total
# number of observations simulations
res_sel <- res_kdd
res_sel$group <- paste0("N = ", res_sel$N, ", n = ", res_sel$n)
group_id <- paste0("N = ", N[fixed_obs], ", n = ", n[fixed_obs])
res_sel <- subset(x = res_sel, subset = group %in% group_id)
res_sel$group <- factor(x = res_sel$group, levels = group_id, ordered = TRUE)
res_sel <- res_sel[order(res_sel$group), ]
res_sel <- split(x = res_sel, f = res_sel$group)
sel <- lapply(
  X = res_sel,
  FUN = function(x) {
    data.frame(
      n = unique(x$group),
      corstr_count(x$sel1)
    )
  }
)
sel <- dplyr::bind_rows(sel)
sel_tab <- knitr::kable(
  x = sel, format = "html",
  col.names = c("N = , n =", legend_work_corstr),
  caption = "Selection properties for Fixed total number of observations"
)
kableExtra::kable_styling(kable_input = sel_tab, full_width = FALSE)
```

#### Comparison 2

For structure selection comparison 2, we are only considering the working correlation structures of *independence*, *exchangeable*, and *AR(1)*.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
# Subsetting the results to only include the results focused on fixed N
# simulations
res_sel <- res_kdd
res_sel$group <- paste0("N = ", res_sel$N, ", n = ", res_sel$n)
group_id <- paste0("N = ", N[fixed_n], ", n = ", n[fixed_n])
res_sel <- subset(x = res_sel, subset = group %in% group_id)
res_sel$group <- factor(x = res_sel$group, levels = group_id, ordered = TRUE)
res_sel <- res_sel[order(res_sel$group), ]
res_sel <- split(x = res_sel, f = res_sel$group)
sel <- lapply(
  X = res_sel,
  FUN = function(x) {
    data.frame(
      n = unique(x$group),
      corstr_count(x$sel2)
    )
  }
)
sel <- dplyr::bind_rows(sel)
sel_tab <- knitr::kable(
  x = sel, format = "html",
  col.names = c("N = 200, n =", legend_work_corstr),
  caption = "Selection properties for Fixed N"
)
kableExtra::kable_styling(kable_input = sel_tab, full_width = FALSE)
```


##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r, echo = FALSE, fig.align = "center", out.width = "100%", warning = FALSE}
# Subsetting the results to only include the results focused on fixed total
# number of observations simulations
res_sel <- res_kdd
res_sel$group <- paste0("N = ", res_sel$N, ", n = ", res_sel$n)
group_id <- paste0("N = ", N[fixed_obs], ", n = ", n[fixed_obs])
res_sel <- subset(x = res_sel, subset = group %in% group_id)
res_sel$group <- factor(x = res_sel$group, levels = group_id, ordered = TRUE)
res_sel <- res_sel[order(res_sel$group), ]
res_sel <- split(x = res_sel, f = res_sel$group)
sel <- lapply(
  X = res_sel,
  FUN = function(x) {
    data.frame(
      n = unique(x$group),
      corstr_count(x$sel2)
    )
  }
)
sel <- dplyr::bind_rows(sel)
sel_tab <- knitr::kable(
  x = sel, format = "html",
  col.names = c("N = , n =", legend_work_corstr),
  caption = "Selection properties for Fixed total number of observations"
)
kableExtra::kable_styling(kable_input = sel_tab, full_width = FALSE)
```

#### Comparison 3

For structure selection comparison 1, we are considering all the working correlation structures of *independence*, *exchangeable*, *AR(1)*, and *AR(3)*.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
# Subsetting the results to only include the results focused on fixed N
# simulations
res_sel <- res_kdd
res_sel$group <- paste0("N = ", res_sel$N, ", n = ", res_sel$n)
group_id <- paste0("N = ", N[fixed_n], ", n = ", n[fixed_n])
res_sel <- subset(x = res_sel, subset = group %in% group_id)
res_sel$group <- factor(x = res_sel$group, levels = group_id, ordered = TRUE)
res_sel <- res_sel[order(res_sel$group), ]
res_sel <- split(x = res_sel, f = res_sel$group)
sel <- lapply(
  X = res_sel,
  FUN = function(x) {
    data.frame(
      n = unique(x$group),
      corstr_count(x$sel3)
    )
  }
)
sel <- dplyr::bind_rows(sel)
sel_tab <- knitr::kable(
  x = sel, format = "html",
  col.names = c("N = 200, n =", legend_work_corstr),
  caption = "Selection properties for Fixed N"
)
kableExtra::kable_styling(kable_input = sel_tab, full_width = FALSE)
```


##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r, echo = FALSE, fig.align = "center", out.width = "100%", warning = FALSE}
# Subsetting the results to only include the results focused on fixed total
# number of observations simulations
res_sel <- res_kdd
res_sel$group <- paste0("N = ", res_sel$N, ", n = ", res_sel$n)
group_id <- paste0("N = ", N[fixed_obs], ", n = ", n[fixed_obs])
res_sel <- subset(x = res_sel, subset = group %in% group_id)
res_sel$group <- factor(x = res_sel$group, levels = group_id, ordered = TRUE)
res_sel <- res_sel[order(res_sel$group), ]
res_sel <- split(x = res_sel, f = res_sel$group)
sel <- lapply(
  X = res_sel,
  FUN = function(x) {
    data.frame(
      n = unique(x$group),
      corstr_count(x$sel3)
    )
  }
)
sel <- dplyr::bind_rows(sel)
sel_tab <- knitr::kable(
  x = sel, format = "html",
  col.names = c("N = , n =", legend_work_corstr),
  caption = "Selection properties for Fixed total number of observations"
)
kableExtra::kable_styling(kable_input = sel_tab, full_width = FALSE)
```

#### Comparison 4

For structure selection comparison 1, we are considering all the working correlation structures of *independence*, *exchangeable*, *AR(1)*, *AR(3)*, and "unstructured".

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
# Subsetting the results to only include the results focused on fixed N
# simulations
res_sel <- res_kdd
res_sel$group <- paste0("N = ", res_sel$N, ", n = ", res_sel$n)
group_id <- paste0("N = ", N[fixed_n], ", n = ", n[fixed_n])
res_sel <- subset(x = res_sel, subset = group %in% group_id)
res_sel$group <- factor(x = res_sel$group, levels = group_id, ordered = TRUE)
res_sel <- res_sel[order(res_sel$group), ]
res_sel <- split(x = res_sel, f = res_sel$group)
sel <- lapply(
  X = res_sel,
  FUN = function(x) {
    data.frame(
      n = unique(x$group),
      corstr_count(x$sel4)
    )
  }
)
sel <- dplyr::bind_rows(sel)
sel_tab <- knitr::kable(
  x = sel, format = "html",
  col.names = c("N = 200, n =", legend_work_corstr),
  caption = "Selection properties for Fixed N"
)
kableExtra::kable_styling(kable_input = sel_tab, full_width = FALSE)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r, echo = FALSE, fig.align = "center", out.width = "100%", warning = FALSE}
# Subsetting the results to only include the results focused on fixed total
# number of observations simulations
res_sel <- res_kdd
res_sel$group <- paste0("N = ", res_sel$N, ", n = ", res_sel$n)
group_id <- paste0("N = ", N[fixed_obs], ", n = ", n[fixed_obs])
res_sel <- subset(x = res_sel, subset = group %in% group_id)
res_sel$group <- factor(x = res_sel$group, levels = group_id, ordered = TRUE)
res_sel <- res_sel[order(res_sel$group), ]
res_sel <- split(x = res_sel, f = res_sel$group)
sel <- lapply(
  X = res_sel,
  FUN = function(x) {
    data.frame(
      n = unique(x$group),
      corstr_count(x$sel4)
    )
  }
)
sel <- dplyr::bind_rows(sel)
sel_tab <- knitr::kable(
  x = sel, format = "html",
  col.names = c("N = , n =", legend_work_corstr),
  caption = "Selection properties for Fixed total number of observations"
)
kableExtra::kable_styling(kable_input = sel_tab, full_width = FALSE)
```

### Generating correlation structure: AR(1) {.tabset .tabset-fade .tabset-pills}
The selection properties of the KDD presented below are based on the data generation process that used an *exchangeable* correlation structure.

```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
# Subsetting the results to only include generating correlation structure
# and covariance estimator of interest
res_kdd <- subset(
  x = res,
  subset = corstr == "ar1"
)
```

#### Comparison 1

For structure selection comparison 1, we are only considering the working correlation structures of *exchangeable* and *AR(1)*.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
# Subsetting the results to only include the results focused on fixed N
# simulations
res_sel <- res_kdd
res_sel$group <- paste0("N = ", res_sel$N, ", n = ", res_sel$n)
group_id <- paste0("N = ", N[fixed_n], ", n = ", n[fixed_n])
res_sel <- subset(x = res_sel, subset = group %in% group_id)
res_sel$group <- factor(x = res_sel$group, levels = group_id, ordered = TRUE)
res_sel <- res_sel[order(res_sel$group), ]
res_sel <- split(x = res_sel, f = res_sel$group)
sel <- lapply(
  X = res_sel,
  FUN = function(x) {
    data.frame(
      n = unique(x$group),
      corstr_count(x$sel1)
    )
  }
)
sel <- dplyr::bind_rows(sel)
sel_tab <- knitr::kable(
  x = sel, format = "html",
  col.names = c("N = 200, n =", legend_work_corstr),
  caption = "Selection properties for Fixed N"
)
kableExtra::kable_styling(kable_input = sel_tab, full_width = FALSE)
```


##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r, echo = FALSE, fig.align = "center", out.width = "100%", warning = FALSE}
# Subsetting the results to only include the results focused on fixed total
# number of observations simulations
res_sel <- res_kdd
res_sel$group <- paste0("N = ", res_sel$N, ", n = ", res_sel$n)
group_id <- paste0("N = ", N[fixed_obs], ", n = ", n[fixed_obs])
res_sel <- subset(x = res_sel, subset = group %in% group_id)
res_sel$group <- factor(x = res_sel$group, levels = group_id, ordered = TRUE)
res_sel <- res_sel[order(res_sel$group), ]
res_sel <- split(x = res_sel, f = res_sel$group)
sel <- lapply(
  X = res_sel,
  FUN = function(x) {
    data.frame(
      n = unique(x$group),
      corstr_count(x$sel1)
    )
  }
)
sel <- dplyr::bind_rows(sel)
sel_tab <- knitr::kable(
  x = sel, format = "html",
  col.names = c("N = , n =", legend_work_corstr),
  caption = "Selection properties for Fixed total number of observations"
)
kableExtra::kable_styling(kable_input = sel_tab, full_width = FALSE)
```

#### Comparison 2

For structure selection comparison 2, we are only considering the working correlation structures of *independence*, *exchangeable*, and *AR(1)*.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
# Subsetting the results to only include the results focused on fixed N
# simulations
res_sel <- res_kdd
res_sel$group <- paste0("N = ", res_sel$N, ", n = ", res_sel$n)
group_id <- paste0("N = ", N[fixed_n], ", n = ", n[fixed_n])
res_sel <- subset(x = res_sel, subset = group %in% group_id)
res_sel$group <- factor(x = res_sel$group, levels = group_id, ordered = TRUE)
res_sel <- res_sel[order(res_sel$group), ]
res_sel <- split(x = res_sel, f = res_sel$group)
sel <- lapply(
  X = res_sel,
  FUN = function(x) {
    data.frame(
      n = unique(x$group),
      corstr_count(x$sel2)
    )
  }
)
sel <- dplyr::bind_rows(sel)
sel_tab <- knitr::kable(
  x = sel, format = "html",
  col.names = c("N = 200, n =", legend_work_corstr),
  caption = "Selection properties for Fixed N"
)
kableExtra::kable_styling(kable_input = sel_tab, full_width = FALSE)
```


##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r, echo = FALSE, fig.align = "center", out.width = "100%", warning = FALSE}
# Subsetting the results to only include the results focused on fixed total
# number of observations simulations
res_sel <- res_kdd
res_sel$group <- paste0("N = ", res_sel$N, ", n = ", res_sel$n)
group_id <- paste0("N = ", N[fixed_obs], ", n = ", n[fixed_obs])
res_sel <- subset(x = res_sel, subset = group %in% group_id)
res_sel$group <- factor(x = res_sel$group, levels = group_id, ordered = TRUE)
res_sel <- res_sel[order(res_sel$group), ]
res_sel <- split(x = res_sel, f = res_sel$group)
sel <- lapply(
  X = res_sel,
  FUN = function(x) {
    data.frame(
      n = unique(x$group),
      corstr_count(x$sel2)
    )
  }
)
sel <- dplyr::bind_rows(sel)
sel_tab <- knitr::kable(
  x = sel, format = "html",
  col.names = c("N = , n =", legend_work_corstr),
  caption = "Selection properties for Fixed total number of observations"
)
kableExtra::kable_styling(kable_input = sel_tab, full_width = FALSE)
```

#### Comparison 3

For structure selection comparison 1, we are considering all the working correlation structures of *independence*, *exchangeable*, *AR(1)*, and *AR(3)*.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
# Subsetting the results to only include the results focused on fixed N
# simulations
res_sel <- res_kdd
res_sel$group <- paste0("N = ", res_sel$N, ", n = ", res_sel$n)
group_id <- paste0("N = ", N[fixed_n], ", n = ", n[fixed_n])
res_sel <- subset(x = res_sel, subset = group %in% group_id)
res_sel$group <- factor(x = res_sel$group, levels = group_id, ordered = TRUE)
res_sel <- res_sel[order(res_sel$group), ]
res_sel <- split(x = res_sel, f = res_sel$group)
sel <- lapply(
  X = res_sel,
  FUN = function(x) {
    data.frame(
      n = unique(x$group),
      corstr_count(x$sel3)
    )
  }
)
sel <- dplyr::bind_rows(sel)
sel_tab <- knitr::kable(
  x = sel, format = "html",
  col.names = c("N = 200, n =", legend_work_corstr),
  caption = "Selection properties for Fixed N"
)
kableExtra::kable_styling(kable_input = sel_tab, full_width = FALSE)
```


##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r, echo = FALSE, fig.align = "center", out.width = "100%", warning = FALSE}
# Subsetting the results to only include the results focused on fixed total
# number of observations simulations
res_sel <- res_kdd
res_sel$group <- paste0("N = ", res_sel$N, ", n = ", res_sel$n)
group_id <- paste0("N = ", N[fixed_obs], ", n = ", n[fixed_obs])
res_sel <- subset(x = res_sel, subset = group %in% group_id)
res_sel$group <- factor(x = res_sel$group, levels = group_id, ordered = TRUE)
res_sel <- res_sel[order(res_sel$group), ]
res_sel <- split(x = res_sel, f = res_sel$group)
sel <- lapply(
  X = res_sel,
  FUN = function(x) {
    data.frame(
      n = unique(x$group),
      corstr_count(x$sel3)
    )
  }
)
sel <- dplyr::bind_rows(sel)
sel_tab <- knitr::kable(
  x = sel, format = "html",
  col.names = c("N = , n =", legend_work_corstr),
  caption = "Selection properties for Fixed total number of observations"
)
kableExtra::kable_styling(kable_input = sel_tab, full_width = FALSE)
```

#### Comparison 4

For structure selection comparison 1, we are considering all the working correlation structures of *independence*, *exchangeable*, *AR(1)*, *AR(3)*, and "unstructured".

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
# Subsetting the results to only include the results focused on fixed N
# simulations
res_sel <- res_kdd
res_sel$group <- paste0("N = ", res_sel$N, ", n = ", res_sel$n)
group_id <- paste0("N = ", N[fixed_n], ", n = ", n[fixed_n])
res_sel <- subset(x = res_sel, subset = group %in% group_id)
res_sel$group <- factor(x = res_sel$group, levels = group_id, ordered = TRUE)
res_sel <- res_sel[order(res_sel$group), ]
res_sel <- split(x = res_sel, f = res_sel$group)
sel <- lapply(
  X = res_sel,
  FUN = function(x) {
    data.frame(
      n = unique(x$group),
      corstr_count(x$sel4)
    )
  }
)
sel <- dplyr::bind_rows(sel)
sel_tab <- knitr::kable(
  x = sel, format = "html",
  col.names = c("N = 200, n =", legend_work_corstr),
  caption = "Selection properties for Fixed N"
)
kableExtra::kable_styling(kable_input = sel_tab, full_width = FALSE)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r, echo = FALSE, fig.align = "center", out.width = "100%", warning = FALSE}
# Subsetting the results to only include the results focused on fixed total
# number of observations simulations
res_sel <- res_kdd
res_sel$group <- paste0("N = ", res_sel$N, ", n = ", res_sel$n)
group_id <- paste0("N = ", N[fixed_obs], ", n = ", n[fixed_obs])
res_sel <- subset(x = res_sel, subset = group %in% group_id)
res_sel$group <- factor(x = res_sel$group, levels = group_id, ordered = TRUE)
res_sel <- res_sel[order(res_sel$group), ]
res_sel <- split(x = res_sel, f = res_sel$group)
sel <- lapply(
  X = res_sel,
  FUN = function(x) {
    data.frame(
      n = unique(x$group),
      corstr_count(x$sel4)
    )
  }
)
sel <- dplyr::bind_rows(sel)
sel_tab <- knitr::kable(
  x = sel, format = "html",
  col.names = c("N = , n =", legend_work_corstr),
  caption = "Selection properties for Fixed total number of observations"
)
kableExtra::kable_styling(kable_input = sel_tab, full_width = FALSE)
```