---
title: "Null distributions for mCIC(R)"
author: "D. Erik Boonstra, MS"
output:
  html_document:
    toc: TRUE
    toc_depth: 4
    toc_float: TRUE
---

```{r, include = FALSE, results = FALSE, message = FALSE}
R <- list.files(path = "./R", pattern = "*.R", full.names = TRUE)
sapply(R, source, .GlobalEnv)
knitr::opts_chunk$set(
  echo = FALSE,
  out.width = "100%",
  fig.align = "center",
  warning = FALSE
)
```

# Purpose
Explore the null distrubtion of the $mCIC(R)$ statistic. The null distribution will be characterized by the $mCIC(R)$ values produced by the working correlation structures that are also the generating correlation structures.

# Definition of mCIC(R)
Let $R(\alpha) = R$ be the working correlation structure, $\hat{\boldsymbol{\beta}}(R)$ be mean parameter estimator given $R$. Furthermore, let the model-based estimated covariance matrix of $\hat{\boldsymbol{\beta}}$ be $\hat{\boldsymbol{\Sigma}}$ and the robust or sandwich estimated covariance matrix of $\hat{\boldsymbol{\beta}}$ be $\hat{\mathbf{V}}_{r}$. Then, following from Hardin and Hilbe, we have

$$
mCIC(R) = trace\left(\hat{\boldsymbol{\Omega}}_{R\mid \hat{\boldsymbol{\beta}} = \hat{\boldsymbol{\beta}}(R)}\hat{\mathbf{V}}_{r\mid \hat{\boldsymbol{\beta}} = \hat{\boldsymbol{\beta}}(R)}\right),
$$

where $\hat{\boldsymbol{\Omega}} = \hat{\boldsymbol{\Sigma}}^{-1}$.

# Presentation of results

## Import results
The null distribution parameters are stored in:
```{r, echo = TRUE}
sub_dir <- "./outputs/corstr/norm-modified-cic-sim/norm-modified-cic-null-dist/"
# Null distribution parameters ####
null_dist <- readRDS(
  file = paste0(
    sub_dir, "norm_modified_cic_null_dist.rds"
  )
)
```
while the realized values from the simulations are store in:
```{r, echo = TRUE}
# Realized values ####
realized <- readRDS(
  file = paste0(
    sub_dir, "norm_modified_cic_realized_values.rds"
  )
)
```

and are dependent on the data generation mechanism (`corstr`) plus the simulation setting defined by the number of non-zero mean parameters and the correlation coefficient (`simulation`).

```{r, include = FALSE}
# indices for all N and n values
fixed_n <- 1:7
fixed_obs <- c(8:9, 3, 10:14)
N <- c(rep(200, 7), 300, 240, 150, 120, 100, 80, 75)
n <- c(4, 5, 6, 7, 8, 9, 10, 4, 5, 8, 10, 12, 15, 16)
set.seed(1997)
```

```{r}
# Cleaning up names of corstr
null_dist$corstr <- ifelse(
  test = null_dist$corstr == "exchangeable",
  yes = "Exchangeable",
  no = "AR(1)"
)
realized$corstr <- ifelse(
  test = realized$corstr == "exchangeable",
  yes = "Exchangeable",
  no = "AR(1)"
)
```

```{r}
# Creating a function to plot ####
plot_all <- function(null, realized, dim_beta, alpha, index, corstr) {
  group_id <- paste0("N = ", N[index], ", n = ", n[index])
  nd <- null
  nd$group <- paste0("N = ", nd$N, ", n = ", nd$n)
  nd <- nd[
    (
      nd$dim_beta == dim_beta &
        nd$alpha == alpha &
        nd$group %in% group_id &
        nd$corstr == corstr
    ),
  ]
  res <- realized
  res$group <- paste0("N = ", res$N, ", n = ", res$n)
  res <- res[
    (
      res$dim_beta == dim_beta &
        res$alpha == alpha &
        res$group %in% group_id &
        res$corstr == corstr
    ),
  ]
  nd_vals <- vector(mode = "list", length = length(group_id))
  for (j in seq_along(group_id)) {
    pars <- subset(
      x = nd, subset = group == group_id[j], select = c(mean, var)
    )
    vals <- rnorm(
      n = 1000, mean = pars$mean, sd = sqrt(pars$var)
    )
    nd_vals[[j]] <- data.frame(
      group = rep(group_id[j], 1000),
      type = rep("Null", 1000),
      mcic = vals
    )
  }
  nd_vals <- dplyr::bind_rows(nd_vals)
  res$type <- "Realized"
  res <- subset(
    x = res,
    select = c(group, type, mcic)
  )
  plot_data <- dplyr::bind_rows(nd_vals, res)
  plot_data$group <- factor(
    x = plot_data$group,
    levels = group_id,
    ordered = TRUE
  )
  ggplot2::ggplot(
    data = plot_data,
    mapping = ggplot2::aes(x = mcic, fill = type)
  ) +
  ggplot2::geom_density(alpha = 0.5, color = NA) +
  ggplot2::facet_wrap(ggplot2::vars(group), ncol = 2, scales = "free_y") +
  ggplot2::labs(
      x = expression(delta),
      y = "Density"
    ) +
    ggplot2::guides(fill = ggplot2::guide_legend(title = "Type of values")) +
    ggplot2::theme_bw()
}
```

```{r}
# Creating functions to generate tables ####

## Null information ####
null_tab <- function(data, dim_beta, alpha, index, corstr) {
  nd <- data
  nd$group <- paste0("N = ", nd$N, ", n = ", nd$n)
  group_id <- paste0("N = ", N[index], ", n = ", n[index])
  nd <- nd[
    (
      nd$dim_beta == dim_beta &
        nd$alpha == alpha &
        nd$group %in% group_id &
        nd$corstr == corstr
    ),
    !(colnames(nd) %in% c("simulation", "group"))
  ]
  nd <- nd[order(nd$n), ]
  row.names(nd) <- NULL

  nd_tab <- knitr::kable(
    x = nd,
    format = "html",
    digits = 4,
    col.names = c(
      "$dim(\\boldsymbol{\\beta})$", "$\\alpha$",
      "N", "n",
      "Correlation structure",
      "$\\mathbb{E}(mCIC(R))$", "$Var(mCIC(R))$"
    ),
    caption = paste0(
      "Null distributional information for $mCIC(R)$ assuming",
      " $mCIC(R) \\sim N(\\mu, \\sigma^{2})$"
    )
  )
  kableExtra::kable_styling(kable_input = nd_tab, full_width = FALSE)
}

## Realized ####
realized_tab <- function(data, dim_beta, alpha, index, corstr) {
  res <- data
  res$group <- paste0("N = ", res$N, ", n = ", res$n)
  group_id <- paste0("N = ", N[index], ", n = ", n[index])
  res <- res[
    (
      res$dim_beta == dim_beta &
        res$alpha == alpha &
        res$group %in% group_id &
        res$corstr == corstr
    ),
    !(colnames(res) %in% c("simulation", "group"))
  ]
  res_tab <- stats::aggregate(
    x = mcic ~ dim_beta + alpha + N + n + corstr,
    data = res,
    FUN = function(x) {
      out <- c(mean(x), stats::var(x))
      names(out) <- c("mean", "var")
      return(out)
    }
  )
  res_tab$mean <- res_tab$mcic[, "mean"]
  res_tab$var <- res_tab$mcic[, "var"]
  res_tab <- subset(x = res_tab, select = colnames(res_tab) != "mcic")
  res_tab <- res_tab[order(res_tab$n), ]
  row.names(res_tab) <- NULL
  res_tab <- knitr::kable(
    x = res_tab,
    format = "html",
    digits = 4,
    col.names = c(
      "$dim(\\boldsymbol{\\beta})$", "$\\alpha$",
      "N", "n",
      "Correlation structure",
      "$\\bar{mCIC(R)}$", "$\\widehat{Var}(mCIC(R))$"
    ),
    caption = paste0(
      "Mean and variance of the realized $mCIC(R)$ values"
    )
  )
  kableExtra::kable_styling(kable_input = res_tab, full_width = FALSE)
}
```

## Examining the distributions of mCIC(R)
In the results below, the null and realized densities of $mCIC(R)$ are plotted with each other along with two tables characterizing the distributions.

### Correlation structure: Exchangeable
The distributions of the mCIC(R) presented below are based on the data generation process that used an *exchangeable* correlation structure.

#### $dim(\boldsymbol{\beta}) = 3, \alpha = 0.5$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 3$, which means the $min(mCIC(R)) = 4$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.5$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_n,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_n,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_n,
  corstr = "Exchangeable"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "Exchangeable"
)
```

#### $dim(\boldsymbol{\beta}) = 3, \alpha = 0.05$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 3$, which means the $min(mCIC(R)) = 4$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.05$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_n,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_n,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_n,
  corstr = "Exchangeable"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "Exchangeable"
)
```

#### $dim(\boldsymbol{\beta}) = 3, \alpha = 0.70$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 3$, which means the $min(mCIC(R)) = 4$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.7$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_n,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_n,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_n,
  corstr = "Exchangeable"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "Exchangeable"
)
```

#### $dim(\boldsymbol{\beta}) = 5, \alpha = 0.5$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 5$, which means the $min(mCIC(R)) = 6$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.5$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_n,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_n,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_n,
  corstr = "Exchangeable"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "Exchangeable"
)
```

#### $dim(\boldsymbol{\beta}) = 5, \alpha = 0.05$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 5$, which means the $min(mCIC(R)) = 6$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.05$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_n,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_n,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_n,
  corstr = "Exchangeable"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "Exchangeable"
)
```

#### $dim(\boldsymbol{\beta}) = 5, \alpha = 0.7$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 5$, which means the $min(mCIC(R)) = 6$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.7$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_n,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_n,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_n,
  corstr = "Exchangeable"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "Exchangeable"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "Exchangeable"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "Exchangeable"
)
```

### Correlation structure: AR(1)
The distributions of the $mCIC(R)$ presented below are based on the data generation process that used an *AR(1)* correlation structure.

#### $dim(\boldsymbol{\beta}) = 3, \alpha = 0.5$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 3$, which means the $min(mCIC(R)) = 4$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.5$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_n,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_n,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_n,
  corstr = "AR(1)"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "AR(1)"
)
```

#### $dim(\boldsymbol{\beta}) = 3, \alpha = 0.05$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 3$, which means the $min(mCIC(R)) = 4$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.05$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_n,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_n,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_n,
  corstr = "AR(1)"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "AR(1)"
)
```

#### $dim(\boldsymbol{\beta}) = 3, \alpha = 0.70$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 3$, which means the $min(mCIC(R)) = 4$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.7$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_n,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_n,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_n,
  corstr = "AR(1)"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 3,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "AR(1)"
)
```

#### $dim(\boldsymbol{\beta}) = 5, \alpha = 0.5$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 5$, which means the $min(mCIC(R)) = 6$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.5$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_n,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_n,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_n,
  corstr = "AR(1)"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.5,
  index = fixed_obs,
  corstr = "AR(1)"
)
```

#### $dim(\boldsymbol{\beta}) = 5, \alpha = 0.05$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 5$, which means the $min(mCIC(R)) = 6$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.05$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_n,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_n,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_n,
  corstr = "AR(1)"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.05,
  index = fixed_obs,
  corstr = "AR(1)"
)
```

#### $dim(\boldsymbol{\beta}) = 5, \alpha = 0.7$
Additionally, we will examine when $dim(\boldsymbol{\beta}) = 5$, which means the $min(mCIC(R)) = 6$ by including the intercept term and the number of non-zero mean parameters, and $\alpha = 0.7$.

##### Fixed N
In these results, the number of subjects does **NOT** change and stays fixed at `r N[1]`. However, the number of observations for each subject has increases from `r n[fixed_n[1]]` to `r n[fixed_n[length(fixed_n)]]` by 1. Thus, the overall number observations is also increasing.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_n,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_n,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_n,
  corstr = "AR(1)"
)
```

##### Fixed total number of observations
In these results, the total number of observations does **NOT** change and stays fixed at `r N[fixed_obs[1]] * n[fixed_obs[1]]`. However, the number of subjects and the number of observations for each subject changes. The numbers of subjects are N: `r N[fixed_obs]` while the number of observations for each subjects are n: `r n[fixed_obs]`.
```{r}
plot_all(
  null = null_dist,
  realized = realized,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "AR(1)"
)

null_tab(
  data = null_dist,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "AR(1)"
)

realized_tab(
  data = realized,
  dim_beta = 5,
  alpha = 0.7,
  index = fixed_obs,
  corstr = "AR(1)"
)
```