---
title: "Simulations investigating the correlation structure selection properties for CIC"
author: "D. Erik Boonstra, MS"
output: html_document 
---

```{r, include = FALSE, results = FALSE, message = FALSE}
R <- list.files(path = "./R", pattern = "*.R", full.names = TRUE)
sapply(R, source, .GlobalEnv)
library(knitr)
library(kableExtra)
```

# Purpose of simulations
The results of these simulations are to investigate the correlation structure selection properties of CIC.

# Simulation setup

## Data
Following Wang *et al.* (2012) with one-thousand replications, the correlated normal responses are generated from the model $$y_{ij} = \mathbf{X}_{ij}^{\top}\boldsymbol{\beta} + \varepsilon_{ij},$$ where $i = 1, \ldots, 200,$ $j = 1, \ldots, 4,$ $\mathbf{X}_{ij} = (x_{ij, 1}, \ldots, x_{ij, 6})^{\top},$ and $\boldsymbol{\beta} = (2.0, 3.0, 0.5, 0.0, 0.0, 0.0)^{\top}.$

- For the covariates,
    - $x_{ij,1}$ was generated from the Bernoulli(0.5) distribution, and 
    - each $x_{ij,k}$ for $k = 2 \ldots 6$ was generated from the multivariate normal distribution with mean 0 and an AR(1) covariance matrix with marginal variance 1 and auto-correlation coefficient 0.5.
- The random errors $(\varepsilon_{i1}, \ldots, \varepsilon_{i4})^{\top}$ are generated from the multivariate normal distribution with marginal mean 0, marginal variance 1, and either an **exchangeable** or **AR(1)** correlation structure with a correlation parameter of $\rho = 0.5$.

```{r, include = FALSE}
nsims <- 1000L
beta <- c(2.0, 3.0, 0.5, 0.0, 0.0, 0.0)
w <- which(beta != 0)
l <- length(w)
```

## Fitting procedure
Considering the focus of these simulations are on the correlation structure selection, each model, based on data generated by an **exchangeable** or **AR(1)** correlation structure, was fitted using generalized estimating equations. The mean structure was properly specified as $\mathbf{X}_{1}$, $\mathbf{X}_{2}$, and $\mathbf{X}_{3}$ with an intercept that was estimated to be approximately 0. To assess the correlation structure selection properties, the working correlation structure was specified as:

- independence,
- exchangeable,
- AR(1), and
- unstrctured.

## Model selection process
In these simulations, there are three sets of comparisons being made between the four correlation structures. These comparisons are:

1. exchangeable versus AR(1),
2. exchangeable versus AR(1) versus independence, and
3. exchangeable versus AR(1) versus independence versus unstrctured.

We are making these comparisons because previous research usually only focuses on exchangeable and AR(1). As these simulations are meant to investigate the selection properties of CIC, for each comparison, the correlation structure that resulted in the minimum CIC value was selected as the best performing correlation structure.

# Presentation of results

## Import results
The simulation results are stored in:
```{r}
load("./outputs/norm_cic_sim/norm_cic_sim.RData")
```

and are dependent on the data generation mechanism. Any simulation results ending in `cs` are based on data generated with the exchangeable correlation structure, and any results ending in `ar1` are based on data generated by the AR(1) correlation structure. Additionally, the numbering of the results are based on the numbered comparisons above. The presentation of the results will be based on the data generation mechanisms of `Exchangeable` and `AR(1)`.

## Distribution of CIC {.tabset .tabset-fade}
The first set of results being presented are the values of CIC for each working correlation structure across the one-thousand replications given the data generation mechanism. The <span style="color: red;">red line</span> in each of the figures is the mean of CIC values for each working correlation structure.

### Generating correlation structure: Exchangeable
```{r, echo = FALSE, fig.align = "center"}
# pulling correlation structure names
work_corstr <- res_cic3_cs[[1]]$corstr
# formatting correlation structure names
legend_work_corstr <- paste0(
  toupper(substr(work_corstr, 1, 1)),
  substr(work_corstr, 2, nchar(work_corstr))
)
legend_work_corstr <- ifelse(
  test = legend_work_corstr == "Ar1",
  yes = "AR(1)", no = legend_work_corstr
)
# plotting values of CIC
cic_all_cs <- matrix(NA, nrow = length(res_cic3_cs), ncol = length(work_corstr))
colnames(cic_all_cs) <- work_corstr
graphics::par(mfrow = c(2, 2))
for (j in seq_len(ncol(cic_all_cs))) {
  cic_all_cs[, j] <- sapply(
    X = res_cic3_cs,
    FUN = function(x) {
      x$ic[which(x$corstr == work_corstr[j])]
    }
  )
  graphics::plot(
    x = seq_len(nsims), y = cic_all_cs[, j],
    xlim = c(0, nsims), ylim = c(2, 8),
    xlab = "Index", ylab = "CIC",
    main = paste0("Working correlation: ", legend_work_corstr[j]),
    type = "p", pch = 16, col = "gray", bty = "n"
  )
  graphics::abline(h = mean(cic_all_cs[, j]), col = "red", lwd = 2)
}
graphics::par(mfrow = c(1, 1))
```

#### Difference criterion values
For the generating correlation structure, we now examine the mean difference of CIC for the working correlation structures. The correlation structure labeled as *Base working correlation* is the working correlation structure that is being compared to the *Other working correlation structures*. Any negative values indicate the CIC value of *Base working correlation* is greater than the CIC value of *Other working correlation structures*.
```{r, echo = FALSE, fig.align = "center"}
x <- cic_all_cs
for (j in seq_len(ncol(x))) {
  w <- which(colnames(x) != colnames(x)[j])
  diff_cs <- matrix(NA, nrow = nrow(x), ncol = ncol(x) - 1)
  colnames(diff_cs) <- colnames(x)[w]
  for (k in seq_len(ncol(diff_cs))) {
    diff_cs[, k] <- x[, w[k]] - x[, j]
  }
  diff_means <- colMeans(diff_cs)
  diff_means <- data.frame(
    type = legend_work_corstr[w],
    means = diff_means
  )
  graphics::barplot(
    formula = means ~ type, data = diff_means, ylim = c(-2, 2),
    border = "white", col = "gray", bty = "n",
    xlab = "Other working correlation structures",
    ylab = "Mean difference in CIC",
    main = paste0("Base working correlation: ", legend_work_corstr[j])
  )
  graphics::abline(h = 0, col = "black", lwd = 0.5, lty = 3)
}
```

### Generating correlation structure: AR(1)
```{r, echo = FALSE, fig.align = "center"}
# pulling correlation structure names
work_corstr <- res_cic3_ar1[[1]]$corstr
# formatting correlation structure names
legend_work_corstr <- paste0(
  toupper(substr(work_corstr, 1, 1)),
  substr(work_corstr, 2, nchar(work_corstr))
)
legend_work_corstr <- ifelse(
  test = legend_work_corstr == "Ar1",
  yes = "AR(1)", no = legend_work_corstr
)
# plotting values of CIC
cic_all_ar1 <- matrix(
  data = NA,
  nrow = length(res_cic3_ar1),
  ncol = length(work_corstr)
)
colnames(cic_all_ar1) <- work_corstr
graphics::par(mfrow = c(2, 2))
for (j in seq_len(ncol(cic_all_ar1))) {
  cic_all_ar1[, j] <- sapply(
    X = res_cic3_ar1,
    FUN = function(x) {
      x$ic[which(x$corstr == work_corstr[j])]
    }
  )
  graphics::plot(
    x = seq_len(nsims), y = cic_all_ar1[, j],
    xlim = c(0, nsims), ylim = c(2, 8),
    xlab = "Index", ylab = "CIC",
    main = paste0("Working correlation: ", legend_work_corstr[j]),
    type = "p", pch = 16, col = "gray", bty = "n"
  )
  graphics::abline(h = mean(cic_all_ar1[, j]), col = "red", lwd = 2)
}
graphics::par(mfrow = c(1, 1))
```

#### Difference criterion values
For the generating correlation structure, we now examine the mean difference of CIC for the working correlation structures. The correlation structure labeled as *Base working correlation* is the working correlation structure that is being compared to the *Other working correlation structures*. Any negative values indicate the CIC value of *Base working correlation* is greater than the CIC value of *Other working correlation structures*.
```{r, echo = FALSE, fig.align = "center"}
x <- cic_all_ar1
for (j in seq_len(ncol(x))) {
  w <- which(colnames(x) != colnames(x)[j])
  diff_cs <- matrix(NA, nrow = nrow(x), ncol = ncol(x) - 1)
  colnames(diff_cs) <- colnames(x)[w]
  for (k in seq_len(ncol(diff_cs))) {
    diff_cs[, k] <- x[, w[k]] - x[, j]
  }
  diff_means <- colMeans(diff_cs)
  diff_means <- data.frame(
    type = legend_work_corstr[w],
    means = diff_means
  )
  graphics::barplot(
    formula = means ~ type, data = diff_means, ylim = c(-2, 2),
    border = "white", col = "gray", bty = "n",
    xlab = "Other working correlation structures",
    ylab = "Mean difference in CIC",
    main = paste0("Base working correlation: ", legend_work_corstr[j])
  )
  graphics::abline(h = 0, col = "black", lwd = 0.5, lty = 3)
}
```

## Correlation structure selection {.tabset .tabset-fade}
Now we will examine the selection properties of CIC given the generating correlation structure and working correlation structures being compared. The comparisons are:

1. exchangeable versus AR(1),
2. exchangeable versus AR(1) versus independence, and
3. exchangeable versus AR(1) versus independence versus unstrctured,

and the results are presented based on the defined numbering system of these comparisons. For each comparison, the hope is the working correlation structure selected by the minimum CIC value is the generating correlation structure the majority of the time.
```{r, echo = FALSE}
corstr_count <- function(x) {
  count_indp <- 0
  count_cs <- 0
  count_ar1 <- 0
  count_un <- 0
  for (i in seq_along(x)) {
    count_indp <- count_indp + (x[i] == "independence")
    count_cs <- count_cs + (x[i] == "exchangeable")
    count_ar1 <- count_ar1 + (x[i] == "ar1")
    count_un <- count_un + (x[i] == "unstructured")
  }
  temp <- data.frame(
    independence = count_indp, exchangeable = count_cs,
    ar1 = count_ar1, un = count_un
  )
  return(temp)
}
```

### Structure comparison 1
```{r, echo = FALSE}
corstr_cic1_cs <- sapply(
  X = res_cic1_cs,
  FUN = function(x) {
    x$corstr_min
  },
  simplify = TRUE
)
corstr_cic1_ar1 <- sapply(
  X = res_cic1_ar1,
  FUN = function(x) {
    x$corstr_min
  },
  simplify = TRUE
)

tab <- data.frame(
  data_gen = c("Exchangeable", "AR(1)"),
  dplyr::bind_rows(corstr_count(corstr_cic1_cs), corstr_count(corstr_cic1_ar1))
)
tab <- subset(x = tab, select = c(data_gen, exchangeable, ar1))
tab <- knitr::kable(
  x = tab, format = "html",
  col.names = c("Generating correlation structure", "Exchangeable", "AR(1)")
)
tab <- kableExtra::kable_styling(
  kable_input = tab,
  full_width = TRUE
)
kableExtra::add_header_above(
  kable_input = tab,
  header = c(" " = 1, "Work correlation structure" = 2),
  align = "c"
)
```

### Structure comparison 2
```{r, echo = FALSE}
corstr_cic2_cs <- sapply(
  X = res_cic2_cs,
  FUN = function(x) {
    x$corstr_min
  },
  simplify = TRUE
)
corstr_cic2_ar1 <- sapply(
  X = res_cic2_ar1,
  FUN = function(x) {
    x$corstr_min
  },
  simplify = TRUE
)

tab <- data.frame(
  data_gen = c("Exchangeable", "AR(1)"),
  dplyr::bind_rows(corstr_count(corstr_cic2_cs), corstr_count(corstr_cic2_ar1))
)
tab <- subset(x = tab, select = c(data_gen, independence, exchangeable, ar1))
tab <- knitr::kable(
  x = tab, format = "html",
  col.names = c(
    "Generating correlation structure", "Independence", "Exchangeable", "AR(1)"
  )
)
tab <- kableExtra::kable_styling(kable_input = tab, full_width = TRUE)
kableExtra::add_header_above(
  kable_input = tab,
  header = c(" " = 1, "Work correlation structure" = 3),
  align = "c"
)
```

### Structure comparison 3
```{r, echo = FALSE}
corstr_cic3_cs <- sapply(
  X = res_cic3_cs,
  FUN = function(x) {
    x$corstr_min
  },
  simplify = TRUE
)
corstr_cic3_ar1 <- sapply(
  X = res_cic3_ar1,
  FUN = function(x) {
    x$corstr_min
  },
  simplify = TRUE
)

tab <- data.frame(
  data_gen = c("Exchangeable", "AR(1)"),
  dplyr::bind_rows(corstr_count(corstr_cic3_cs), corstr_count(corstr_cic3_ar1))
)
tab <- knitr::kable(
  x = tab, format = "html",
  col.names = c(
    "Generating correlation structure", "Independence", "Exchangeable", "AR(1)",
    "Unstructured"
  )
)
tab <- kableExtra::kable_styling(kable_input = tab, full_width = TRUE)
kableExtra::add_header_above(
  kable_input = tab,
  header = c(" " = 1, "Work correlation structure" = 4),
  align = "c"
)
```