---
title: "Simulations investigating the correlation structure selection properties for $\\delta$"
author: "D. Erik Boonstra, MS"
output:
  html_document:
    toc: TRUE
    toc_depth: 2
    toc_float: TRUE
---

```{r, include = FALSE, results = FALSE, message = FALSE}
R <- list.files(path = "./R", pattern = "*.R", full.names = TRUE)
sapply(R, source, .GlobalEnv)
```

# Purpose of simulations
The results of these simulations are to investigate the correlation structure selection properties of a new measure called $\delta$. The name of this measure might evolve if the results are promising.

# Definition of $\delta$
Given two square matrices, $\mathbf{A}$ and $\mathbf{B}$, of the same dimension, $d$, let $\delta$ be define as the following:
$$
\delta(\mathbf{A}, \mathbf{B}) = \sum_{i = 1}^{d} max\left(\frac{b_{ii}}{a_{ii}}, \frac{a_{ii}}{b_{ii}}\right),
$$

where $a_{ii}$ and $b_{ii}$ are the diagonal elements of the matrices $\mathbf{A}$ and $\mathbf{B}$. The minimum value for $\delta$ will be the dimension of the matrices $d$. This minimum will be achieved if $a_{ii} \approx b_{ii}$ for all $i$. By the definition of $\delta$, this measure is a symmetric discrepancy.

## $\delta$ for GEEs
Let $R(\alpha) = R$ be the working correlation structure and $\hat{\boldsymbol{\beta}}(R)$ be mean parameter estimator given $R$. Furthermore, let the model-based estimated covariance matrix of $\hat{\boldsymbol{\beta}}$ be $\hat{\boldsymbol{\Sigma}}$ and the robust or sandwich estimated covariance matrix of $\hat{\boldsymbol{\beta}}$ be $\hat{\mathbf{V}}_{r}$. Then, in the generalized estimating equations (GEEs) setting, we hope $\delta$ will be able to select the proper correlation structure by comparing the model-based covariance matrix, $\hat{\boldsymbol{\Sigma}}$, given $\hat{\boldsymbol{\beta}}(R)$ to the robust covariance matrix, $\hat{\mathbf{V}}_{r}$, given $\hat{\boldsymbol{\beta}}(R)$. The robust covariance matrix $\hat{\mathbf{V}}_{r}$ protects against misspecification of the working correlation structure while the variance estimates for the model-based covariance matrix $\hat{\boldsymbol{\Sigma}}$ could vary drastically based on the working correlation structure. If $\delta \approx k$, where $k$ is the dimension of the parameter vector $\boldsymbol{\beta}$, then one would be able to assume that $\boldsymbol{\Sigma} \approx \mathbf{V}_{r}$ and the working correlation structure is appropriate given the mean structure is specified properly. The use of $\delta$ in the GEEs setting is reasonable because the mean structure estimates are protected against misspecification of the correlation structure and proper selection of correlation structure provides gains in efficiency not accuracy of statistical inference.

# Simulation setup

## Data
Following Wang *et al.* (2012) with one-thousand replications, the correlated normal responses are generated from the model $$y_{ij} = \mathbf{X}_{ij}^{\top}\boldsymbol{\beta} + \varepsilon_{ij},$$ where $i = 1, \ldots, 200,$ $j = 1, \ldots, 4,$ $\mathbf{X}_{ij} = (x_{ij, 1}, \ldots, x_{ij, 6})^{\top},$ and $\boldsymbol{\beta} = (2.0, 3.0, 0.5, 0.0, 0.0, 0.0)^{\top}.$

- For the covariates,
    - $x_{ij,1}$ was generated from the Bernoulli(0.5) distribution, and 
    - each $x_{ij,k}$ for $k = 2 \ldots 6$ was generated from the multivariate normal distribution with mean 0 and an AR(1) covariance matrix with marginal variance 1 and auto-correlation coefficient 0.5.
- The random errors $(\varepsilon_{i1}, \ldots, \varepsilon_{i4})^{\top}$ are generated from the multivariate normal distribution with marginal mean 0, marginal variance 1, and either an **exchangeable** or **AR(1)** correlation structure with a correlation parameter of $\alpha = 0.5$.

```{r, include = FALSE}
nsims <- 1000L
beta <- c(2.0, 3.0, 0.5, 0.0, 0.0, 0.0)
w <- which(beta != 0)
l <- length(w)
```

## Fitting procedure
Considering the focus of these simulations are on the correlation structure selection, each model, based on data generated by an **exchangeable** or **AR(1)** correlation structure, was fitted using generalized estimating equations. The mean structure was properly specified as $\mathbf{X}_{1}$, $\mathbf{X}_{2}$, and $\mathbf{X}_{3}$ with an intercept that was estimated to be approximately 0. To assess the correlation structure selection properties, the working correlation structure was specified as:

- independence,
- exchangeable,
- AR(1), and
- unstrctured.

## Model selection process
In these simulations, there are three sets of comparisons being made between the four correlation structures. These comparisons are:

1. exchangeable versus AR(1),
2. exchangeable versus AR(1) versus independence, and
3. exchangeable versus AR(1) versus independence versus unstrctured.

We are making these comparisons because previous research usually only focuses on exchangeable and AR(1). As these simulations are meant to investigate the selection properties of $\delta$, for each comparison, the correlation structure that resulted in the minimum $\delta$ value was selected as the best performing correlation structure.

# Presentation of results

## Import results
The simulation results are stored in:
```{r}
load("./outputs/corstr/norm-delta-sim/norm_delta_sim.RData")
```

and are dependent on the data generation mechanism. Any simulation results ending in `cs` are based on data generated with the exchangeable correlation structure, and any results ending in `ar1` are based on data generated by the AR(1) correlation structure. Additionally, the numbering of the results are based on the numbered comparisons above. The presentation of the results will be based on the data generation mechanisms of *exchangeable* and *AR(1)*.

## Distribution of $\delta$ {.tabset .tabset-fade}
The first set of results being presented are the values of $\delta$ for each working correlation structure across the one-thousand replications given the data generation mechanism. The <span style="color: red;">red line</span> in each of the figures is the mean of the orcale $\delta$ values for each working correlation structure.

### Generating correlation structure: Exchangeable
```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
# pulling correlation structure names
work_corstr <- res_delta3_cs[[1]]$corstr
# formatting correlation structure names
legend_work_corstr <- paste0(
  toupper(substr(work_corstr, 1, 1)),
  substr(work_corstr, 2, nchar(work_corstr))
)
legend_work_corstr <- ifelse(
  test = legend_work_corstr == "Ar1",
  yes = "AR(1)", no = legend_work_corstr
)
# plotting values of delta
delta_all_cs <- matrix(
  data = NA,
  nrow = length(res_delta3_cs),
  ncol = length(work_corstr)
)
colnames(delta_all_cs) <- work_corstr
graphics::par(mfrow = c(2, 2))
for (j in seq_len(ncol(delta_all_cs))) {
  delta_all_cs[, j] <- sapply(
    X = res_delta3_cs,
    FUN = function(x) {
      x$ic[which(x$corstr == work_corstr[j])]
    }
  )
  graphics::plot(
    x = seq_len(nsims), y = delta_all_cs[, j],
    xlim = c(0, nsims), ylim = c(2, 8),
    xlab = "Index", ylab = expression(delta),
    main = paste0("Working correlation: ", legend_work_corstr[j]),
    type = "p", pch = 16, col = "gray", bty = "n"
  )
  graphics::abline(h = mean(res_delta0_cs[, j]), col = "red", lwd = 2)
}
graphics::par(mfrow = c(1, 1))
tab1 <- apply(
  X = delta_all_cs,
  MARGIN = 2,
  FUN = function(x) c(mean(x), var(x))
)
tab2 <- apply(
  X = res_delta0_cs,
  MARGIN = 2,
  FUN = function(x) c(mean(x), var(x))
)
tab3 <- tab1[1, ] - tab2[1, ]
tab <- data.frame(
  stat = c(rep(c("Mean", "Variance"), 2), "Difference in mean"),
  type = c("Realized", "Realized", "Orcale", "Orcale", "Realized - Orcale"),
  rbind(tab1, tab2, tab3)
)
row.names(tab) <- NULL
tab <- knitr::kable(
  x = tab,
  format = "html",
  col.names = c("Statistic", "$\\delta$ type", legend_work_corstr)
)
kableExtra::kable_styling(tab)
```

#### Difference in criterion values
For the generating correlation structure, we now examine the mean difference of $\delta$ for the working correlation structures. The correlation structure labeled as *Base working correlation* is the working correlation structure that is being compared to the *Other working correlation structures*. Any negative values indicate the $\delta$ values of *Base working correlation* are greater than the $\delta$ values of *Other working correlation structures*.
```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
x <- delta_all_cs
for (j in seq_len(ncol(x))) {
  w <- which(colnames(x) != colnames(x)[j])
  diff_cs <- matrix(NA, nrow = nrow(x), ncol = ncol(x) - 1)
  colnames(diff_cs) <- colnames(x)[w]
  for (k in seq_len(ncol(diff_cs))) {
    diff_cs[, k] <- x[, w[k]] - x[, j]
  }
  diff_means <- colMeans(diff_cs)
  diff_means <- data.frame(
    type = legend_work_corstr[w],
    means = diff_means
  )
  graphics::barplot(
    formula = means ~ type, data = diff_means, ylim = c(-3, 3),
    border = "white", col = "gray", bty = "n",
    xlab = "Other working correlation structures",
    ylab = expression("Mean difference in" ~ delta),
    main = paste0("Base working correlation: ", legend_work_corstr[j])
  )
  graphics::abline(h = 0, col = "black", lwd = 0.5, lty = 3)
  graphics::abline(h = 2, col = "firebrick", lwd = 0.5, lty = 2)
  graphics::abline(h = -2, col = "firebrick", lwd = 0.5, lty = 2)
}
```

### Generating correlation structure: AR(1)
```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
# pulling correlation structure names
work_corstr <- res_delta3_ar1[[1]]$corstr
# formatting correlation structure names
legend_work_corstr <- paste0(
  toupper(substr(work_corstr, 1, 1)),
  substr(work_corstr, 2, nchar(work_corstr))
)
legend_work_corstr <- ifelse(
  test = legend_work_corstr == "Ar1",
  yes = "AR(1)", no = legend_work_corstr
)
# plotting values of delta
delta_all_ar1 <- matrix(
  data = NA,
  nrow = length(res_delta3_ar1),
  ncol = length(work_corstr)
)
colnames(delta_all_ar1) <- work_corstr
graphics::par(mfrow = c(2, 2))
for (j in seq_len(ncol(delta_all_ar1))) {
  delta_all_ar1[, j] <- sapply(
    X = res_delta3_ar1,
    FUN = function(x) {
      x$ic[which(x$corstr == work_corstr[j])]
    }
  )
  graphics::plot(
    x = seq_len(nsims), y = delta_all_ar1[, j],
    xlim = c(0, nsims), ylim = c(2, 8),
    xlab = "Index", ylab = expression(delta),
    main = paste0("Working correlation: ", legend_work_corstr[j]),
    type = "p", pch = 16, col = "gray", bty = "n"
  )
  graphics::abline(h = mean(res_delta0_ar1[, j]), col = "red", lwd = 2)
}
graphics::par(mfrow = c(1, 1))
tab1 <- apply(
  X = delta_all_ar1,
  MARGIN = 2,
  FUN = function(x) c(mean(x), var(x))
)
tab2 <- apply(
  X = res_delta0_ar1,
  MARGIN = 2,
  FUN = function(x) c(mean(x), var(x))
)
tab3 <- tab1[1, ] - tab2[1, ]
tab <- data.frame(
  stat = c(rep(c("Mean", "Variance"), 2), "Difference in mean"),
  type = c("Realized", "Realized", "Orcale", "Orcale", "Realized - Orcale"),
  rbind(tab1, tab2, tab3)
)
row.names(tab) <- NULL
tab <- knitr::kable(
  x = tab,
  format = "html",
  col.names = c("Statistic", "$\\delta$ type", legend_work_corstr)
)
kableExtra::kable_styling(tab)
```

#### Difference in criterion values
For the generating correlation structure, we now examine the mean difference of $\delta$ for the working correlation structures. The correlation structure labeled as *Base working correlation* is the working correlation structure that is being compared to the *Other working correlation structures*. Any negative values indicate the $\delta$ values of *Base working correlation* are greater than the $\delta$ values of *Other working correlation structures*.
```{r, echo = FALSE, fig.align = "center", out.width = "100%"}
x <- delta_all_ar1
for (j in seq_len(ncol(x))) {
  w <- which(colnames(x) != colnames(x)[j])
  diff_ar1 <- matrix(NA, nrow = nrow(x), ncol = ncol(x) - 1)
  colnames(diff_ar1) <- colnames(x)[w]
  for (k in seq_len(ncol(diff_ar1))) {
    diff_ar1[, k] <- x[, w[k]] - x[, j]
  }
  diff_means <- colMeans(diff_ar1)
  diff_means <- data.frame(
    type = legend_work_corstr[w],
    means = diff_means
  )
  graphics::barplot(
    formula = means ~ type, data = diff_means, ylim = c(-3, 3),
    border = "white", col = "gray", bty = "n",
    xlab = "Other working correlation structures",
    ylab = expression("Mean difference in" ~ delta),
    main = paste0("Base working correlation: ", legend_work_corstr[j])
  )
  graphics::abline(h = 0, col = "black", lwd = 0.5, lty = 3)
  graphics::abline(h = 2, col = "firebrick", lwd = 0.5, lty = 2)
  graphics::abline(h = -2, col = "firebrick", lwd = 0.5, lty = 2)
}
```

## Correlation structure selection {.tabset .tabset-fade}
Now we will examine the selection properties of $\delta$ given the generating correlation structure and working correlation structures being compared. The comparisons are:

1. exchangeable versus AR(1),
2. exchangeable versus AR(1) versus independence, and
3. exchangeable versus AR(1) versus independence versus unstrctured,

and the results are presented based on the defined numbering system of these comparisons. For each comparison, the hope is the working correlation structure selected by the minimum $\delta$ value is the generating correlation structure the majority of the time.
```{r, echo = FALSE}
corstr_count <- function(x) {
  count_indp <- 0
  count_cs <- 0
  count_ar1 <- 0
  count_un <- 0
  for (i in seq_along(x)) {
    count_indp <- count_indp + (x[i] == "independence")
    count_cs <- count_cs + (x[i] == "exchangeable")
    count_ar1 <- count_ar1 + (x[i] == "ar1")
    count_un <- count_un + (x[i] == "unstructured")
  }
  temp <- data.frame(
    independence = count_indp, exchangeable = count_cs,
    ar1 = count_ar1, un = count_un
  )
  return(temp)
}
```

### Structure comparison 1
```{r, echo = FALSE}
corstr_delta1_cs <- sapply(
  X = res_delta1_cs,
  FUN = function(x) {
    x$corstr_min
  },
  simplify = TRUE
)
corstr_delta1_ar1 <- sapply(
  X = res_delta1_ar1,
  FUN = function(x) {
    x$corstr_min
  },
  simplify = TRUE
)

tab <- data.frame(
  data_gen = c("Exchangeable", "AR(1)"),
  dplyr::bind_rows(
    corstr_count(corstr_delta1_cs),
    corstr_count(corstr_delta1_ar1)
  )
)
tab <- subset(x = tab, select = c(data_gen, exchangeable, ar1))
tab <- knitr::kable(
  x = tab, format = "html",
  col.names = c("Generating correlation structure", "Exchangeable", "AR(1)")
)
tab <- kableExtra::kable_styling(
  kable_input = tab,
  full_width = TRUE
)
kableExtra::add_header_above(
  kable_input = tab,
  header = c(" " = 1, "Work correlation structure" = 2),
  align = "c"
)
```

### Structure comparison 2
```{r, echo = FALSE}
corstr_delta2_cs <- sapply(
  X = res_delta2_cs,
  FUN = function(x) {
    x$corstr_min
  },
  simplify = TRUE
)
corstr_delta2_ar1 <- sapply(
  X = res_delta2_ar1,
  FUN = function(x) {
    x$corstr_min
  },
  simplify = TRUE
)

tab <- data.frame(
  data_gen = c("Exchangeable", "AR(1)"),
  dplyr::bind_rows(
    corstr_count(corstr_delta2_cs),
    corstr_count(corstr_delta2_ar1)
  )
)
tab <- subset(x = tab, select = c(data_gen, independence, exchangeable, ar1))
tab <- knitr::kable(
  x = tab, format = "html",
  col.names = c(
    "Generating correlation structure", "Independence", "Exchangeable", "AR(1)"
  )
)
tab <- kableExtra::kable_styling(kable_input = tab, full_width = TRUE)
kableExtra::add_header_above(
  kable_input = tab,
  header = c(" " = 1, "Work correlation structure" = 3),
  align = "c"
)
```

### Structure comparison 3
```{r, echo = FALSE}
corstr_delta3_cs <- sapply(
  X = res_delta3_cs,
  FUN = function(x) {
    x$corstr_min
  },
  simplify = TRUE
)
corstr_delta3_ar1 <- sapply(
  X = res_delta3_ar1,
  FUN = function(x) {
    x$corstr_min
  },
  simplify = TRUE
)

tab <- data.frame(
  data_gen = c("Exchangeable", "AR(1)"),
  dplyr::bind_rows(
    corstr_count(corstr_delta3_cs),
    corstr_count(corstr_delta3_ar1)
  )
)
tab <- knitr::kable(
  x = tab, format = "html",
  col.names = c(
    "Generating correlation structure", "Independence", "Exchangeable", "AR(1)",
    "Unstructured"
  )
)
tab <- kableExtra::kable_styling(kable_input = tab, full_width = TRUE)
kableExtra::add_header_above(
  kable_input = tab,
  header = c(" " = 1, "Work correlation structure" = 4),
  align = "c"
)
```