---
output: html_document
---

# Simulations for `norm_glsx_bqicu_sim.R`
```{r loading packages, include = FALSE}
R <- list.files(path = "./R", pattern = "*.R", full.names = TRUE)
sapply(R, source, .GlobalEnv)
library(knitr)
library(kableExtra)
```

## Setting

### Data
Following Wang *et al.* (2012) with one-hundred replications, the correlated normal responses are generated from the model $$y_{ij} = \mathbf{X}_{ij}^{\top}\boldsymbol{\beta} + \varepsilon_{ij},$$ where $i = 1, \ldots, 200,$ $j = 1, \ldots, 4,$ $\mathbf{X}_{ij} = (x_{ij, 1}, \ldots, x_{ij, 6})^{\top},$ and $\boldsymbol{\beta} = (2.0, 3.0, 0.5, 0.0, 0.0, 0.0)^{\top}.$

- For the covariates,
    - $x_{ij,1}$ was generated from the Bernoulli(0.5) distribution, and 
    - $x_{ij,2}$ to $x_{ij,6}$ from the multivariate normal distribution with mean 0 and an AR(1) covariance matrix with marginal variance 1 and auto-correlation coefficient 0.5.
- The random errors $(\varepsilon_{i1}, \ldots, \varepsilon_{i4})^{\top}$ are generated from the multivariate normal distribution with marginal mean 0, marginal variance 1, and an exchangeable correlation matrix with $\rho = 0.5$.

### Transformation of the response and covariate matrix
After the data was simulated, the response, $\mathbf{y},$ and the covariate matrix, $\mathbf{X},$ was transformed by:

1. fitting a fully saturated model with an unstructured working correlation matrix,
2. calculating $\mathbf{V}_{i} = \phi \mathbf{A}_{i}^{1/2}\mathbf{R}_{i}(\boldsymbol{\alpha})\mathbf{A}_{i}^{1/2}$ and finding $\mathbf{V}_{i}^{-1/2}$, and
3. obtaining $\mathbf{y}^{*} = \mathbf{V}_{i}^{-1/2}\mathbf{y}$ and $\mathbf{X}^{*} = \mathbf{V}_{i}^{-1/2}\mathbf{X}$.

These simulations are different from `norm_gls_sim` and `norm_gls_bqicu_sim` because the covariate matrix is also being transformed.

### Best subsets
Using the transformed response and covariate matrix, all $2^6 - 1 = 63$ the subsets of the fully saturated model were fit using either an independence, exchangeable, or AR(1) working correlation structure. Then, the model resulting in the minimum QIC, QICu, and BQICu value were selected as the best fitting models.

```{r, echo = FALSE}
nsims <- 100L
beta <- c(2.0, 3.0, 0.5, 0.0, 0.0, 0.0)
w <- which(beta != 0)
l <- length(w)
```

## Results
The simulations results are stored in:
```{r loading sim res}
load("./outputs/norm_glsx_bqicu_sim/norm_glsx_bqicu_sim.RData")
```

### Information criterions across the simulations
Now for each of the models with the minimum QIC, QICu and BQICu, the information criteria values will be broken into their parts to see what is impacting the selection process. Additionally, this provides a look at the stability of the information criterions across the simulations. QICu and BQICu have the same goodness-of-fit term (GOF) as QIC (2001a)
$$
GOF = -2 * \text{quasi-likelihood},
$$
which assumes independence among the response to allow the use of the quasi-likelihood framework. The penalty term for QIC is $2tr\left(\widehat{\boldsymbol{\Omega}}_{I}\widehat{\mathbf{V}}_{R}\right)$However, QICu and BQICu replace the penalty term of QIC with $2p$ and $\log(N)p,$ respectively, where $p$ is the number of parameters in the model.

#### QIC
```{r, echo = FALSE}
qic_indp <- sapply(res_indp_qic, function(x) {x$qic_min}, simplify = TRUE)
qic_ar1 <- sapply(res_ar1_qic, function(x) {x$qic_min}, simplify = TRUE)
qic_cs <- sapply(res_cs_qic, function(x) {x$qic_min}, simplify = TRUE)

plot(
    x = seq_len(nsims), y = qic_indp,
    ylim = c(600, 1000),
    xlab = "Index", ylab = "QIC",
    type = "l", lwd = 2, col = "gray",
    bty = "n",
)
lines(
    x = seq_len(nsims), y = qic_ar1,
    col = "firebrick", lwd = 2
)
lines(
    x = seq_len(nsims), y = qic_cs,
    col = "steelblue4", lwd = 2
)
legend_top(
    legend = c("Independence", "Exchangeable", "AR(1)"),
    col = c("gray", "steelblue4", "firebrick"),
    lwd = 2, lty = 1, title = "Working correlation structure"
)
```

#### QICu
```{r, echo = FALSE}
qicu_indp <- sapply(res_indp_qicu, function(x) {x$qicu_min}, simplify = TRUE)
qicu_ar1 <- sapply(res_ar1_qicu, function(x) {x$qicu_min}, simplify = TRUE)
qicu_cs <- sapply(res_cs_qicu, function(x) {x$qicu_min}, simplify = TRUE)

plot(
    x = seq_len(nsims), y = qicu_indp,
    ylim = c(600, 1000),
    xlab = "Index", ylab = "QICu",
    type = "l", lwd = 2, col = "gray",
    bty = "n",
)
lines(
    x = seq_len(nsims), y = qicu_ar1,
    col = "firebrick", lwd = 2
)
lines(
    x = seq_len(nsims), y = qicu_cs,
    col = "steelblue4", lwd = 2
)
legend_top(
    legend = c("Independence", "Exchangeable", "AR(1)"),
    col = c("gray", "steelblue4", "firebrick"),
    lwd = 2, lty = 1, title = "Working correlation structure"
)
```

#### BQICu
```{r, echo = FALSE}
bqicu_indp <- sapply(res_indp_bqicu, function(x) {x$bqicu_min}, simplify = TRUE)
bqicu_ar1 <- sapply(res_ar1_bqicu, function(x) {x$bqicu_min}, simplify = TRUE)
bqicu_cs <- sapply(res_cs_bqicu, function(x) {x$bqicu_min}, simplify = TRUE)

plot(
    x = seq_len(nsims), y = bqicu_indp,
    ylim = c(600, 1000),
    xlab = "Index", ylab = "BQICu",
    type = "l", lwd = 2, col = "gray",
    bty = "n",
)
lines(
    x = seq_len(nsims), y = bqicu_ar1,
    col = "firebrick", lwd = 2
)
lines(
    x = seq_len(nsims), y = bqicu_cs,
    col = "steelblue4", lwd = 2
)
legend_top(
    legend = c("Independence", "Exchangeable", "AR(1)"),
    col = c("gray", "steelblue4", "firebrick"),
    lwd = 2, lty = 1, title = "Working correlation structure"
)
```

#### Goodness-of-fit {.tabset .tabset-fade .tabset-pills}

##### QIC
```{r, echo = FALSE}
gof_indp <- rep(NA, nsims)
gof_ar1 <- rep(NA, nsims)
gof_cs <- rep(NA, nsims)
for (k in seq_len(nsims)) {
    w1 <- res_indp_qic[[k]]$min
    w2 <- res_ar1_qic[[k]]$min
    w3 <- res_cs_qic[[k]]$min
    gof_indp[k] <- res_indp_qic[[k]]$gof[w1]
    gof_ar1[k] <- res_ar1_qic[[k]]$gof[w2]
    gof_cs[k] <- res_cs_qic[[k]]$gof[w3]
}

plot(
    x = seq_len(nsims), y = gof_indp,
    ylim = c(600, 1000),
    xlab = "Index", ylab = "GOF",
    type = "l", lwd = 2, col = "gray",
    bty = "n"
)
lines(
    x = seq_len(nsims), y = gof_ar1,
    col = "firebrick", lwd = 2
)
lines(
    x = seq_len(nsims), y = gof_cs,
    col = "steelblue4", lwd = 2
)
legend_top(
    legend = c("Independence", "Exchangeable", "AR(1)"),
    col = c("gray", "steelblue4", "firebrick"),
    lwd = 2, lty = 1, title = "Working correlation structure"
)
```

##### QICu
```{r, echo = FALSE}
gof_indp <- rep(NA, nsims)
gof_ar1 <- rep(NA, nsims)
gof_cs <- rep(NA, nsims)
for (k in seq_len(nsims)) {
    w1 <- res_indp_qicu[[k]]$min
    w2 <- res_ar1_qicu[[k]]$min
    w3 <- res_cs_qicu[[k]]$min
    gof_indp[k] <- res_indp_qicu[[k]]$gof[w1]
    gof_ar1[k] <- res_ar1_qicu[[k]]$gof[w2]
    gof_cs[k] <- res_cs_qicu[[k]]$gof[w3]
}

plot(
    x = seq_len(nsims), y = gof_indp,
    ylim = c(600, 1000),
    xlab = "Index", ylab = "GOF",
    type = "l", lwd = 2, col = "gray",
    bty = "n"
)
lines(
    x = seq_len(nsims), y = gof_ar1,
    col = "firebrick", lwd = 2
)
lines(
    x = seq_len(nsims), y = gof_cs,
    col = "steelblue4", lwd = 2
)
legend_top(
    legend = c("Independence", "Exchangeable", "AR(1)"),
    col = c("gray", "steelblue4", "firebrick"),
    lwd = 2, lty = 1, title = "Working correlation structure"
)
```

##### BQICu
```{r, echo = FALSE}
gof_indp <- rep(NA, nsims)
gof_ar1 <- rep(NA, nsims)
gof_cs <- rep(NA, nsims)
for (k in seq_len(nsims)) {
    w1 <- res_indp_bqicu[[k]]$min
    w2 <- res_ar1_bqicu[[k]]$min
    w3 <- res_cs_bqicu[[k]]$min
    gof_indp[k] <- res_indp_bqicu[[k]]$gof[w1]
    gof_ar1[k] <- res_ar1_bqicu[[k]]$gof[w2]
    gof_cs[k] <- res_cs_bqicu[[k]]$gof[w3]
}

plot(
    x = seq_len(nsims), y = gof_indp,
    ylim = c(600, 1000),
    xlab = "Index", ylab = "GOF",
    type = "l", lwd = 2, col = "gray",
    bty = "n"
)
lines(
    x = seq_len(nsims), y = gof_ar1,
    col = "firebrick", lwd = 2
)
lines(
    x = seq_len(nsims), y = gof_cs,
    col = "steelblue4", lwd = 2
)
legend_top(
    legend = c("Independence", "Exchangeable", "AR(1)"),
    col = c("gray", "steelblue4", "firebrick"),
    lwd = 2, lty = 1, title = "Working correlation structure"
)
```

#### Penalty {.tabset .tabset-fade .tabset-pills}

##### QIC
```{r, echo = FALSE}
penalty_indp <- rep(NA, nsims)
penalty_ar1 <- rep(NA, nsims)
penalty_cs <- rep(NA, nsims)
for (k in seq_len(nsims)) {
    w1 <- res_indp_qic[[k]]$min
    w2 <- res_ar1_qic[[k]]$min
    w3 <- res_cs_qic[[k]]$min
    penalty_indp[k] <- res_indp_qic[[k]]$penalty[w1]
    penalty_ar1[k] <- res_ar1_qic[[k]]$penalty[w2]
    penalty_cs[k] <- res_cs_qic[[k]]$penalty[w3]
}

plot(
    x = seq_len(nsims), y = penalty_indp,
    ylim = c(0, 15),
    xlab = "Index", ylab = "Penalty",
    type = "l", lwd = 2, col = "gray",
    bty = "n"
)
lines(
    x = seq_len(nsims), y = penalty_ar1,
    col = "firebrick", lwd = 2
)
lines(
    x = seq_len(nsims), y = penalty_cs,
    col = "steelblue4", lwd = 2
)
legend_top(
    legend = c("Independence", "Exchangeable", "AR(1)"),
    col = c("gray", "steelblue4", "firebrick"),
    lwd = 2, lty = 1, title = "Working correlation structure"
)
```

##### QICu
```{r, echo = FALSE}
penalty_indp <- rep(NA, nsims)
penalty_ar1 <- rep(NA, nsims)
penalty_cs <- rep(NA, nsims)
for (k in seq_len(nsims)) {
    w1 <- res_indp_qicu[[k]]$min
    w2 <- res_ar1_qicu[[k]]$min
    w3 <- res_cs_qicu[[k]]$min
    penalty_indp[k] <- res_indp_qicu[[k]]$penalty[w1]
    penalty_ar1[k] <- res_ar1_qicu[[k]]$penalty[w2]
    penalty_cs[k] <- res_cs_qicu[[k]]$penalty[w3]
}

plot(
    x = seq_len(nsims), y = penalty_indp,
    ylim = c(0, 15),
    xlab = "Index", ylab = "Penalty",
    type = "l", lwd = 2, col = "gray",
    bty = "n"
)
lines(
    x = seq_len(nsims), y = penalty_ar1,
    col = "firebrick", lwd = 2
)
lines(
    x = seq_len(nsims), y = penalty_cs,
    col = "steelblue4", lwd = 2
)
legend_top(
    legend = c("Independence", "Exchangeable", "AR(1)"),
    col = c("gray", "steelblue4", "firebrick"),
    lwd = 2, lty = 1, title = "Working correlation structure"
)
```

##### BQICu
```{r, echo = FALSE}
penalty_indp <- rep(NA, nsims)
penalty_ar1 <- rep(NA, nsims)
penalty_cs <- rep(NA, nsims)
for (k in seq_len(nsims)) {
    w1 <- res_indp_bqicu[[k]]$min
    w2 <- res_ar1_bqicu[[k]]$min
    w3 <- res_cs_bqicu[[k]]$min
    penalty_indp[k] <- res_indp_bqicu[[k]]$penalty[w1]
    penalty_ar1[k] <- res_ar1_bqicu[[k]]$penalty[w2]
    penalty_cs[k] <- res_cs_bqicu[[k]]$penalty[w3]
}

plot(
    x = seq_len(nsims), y = penalty_indp,
    ylim = c(20, 35),
    xlab = "Index", ylab = "Penalty",
    type = "l", lwd = 2, col = "gray",
    bty = "n"
)
lines(
    x = seq_len(nsims), y = penalty_ar1,
    col = "firebrick", lwd = 2
)
lines(
    x = seq_len(nsims), y = penalty_cs,
    col = "steelblue4", lwd = 2
)
legend_top(
    legend = c("Independence", "Exchangeable", "AR(1)"),
    col = c("gray", "steelblue4", "firebrick"),
    lwd = 2, lty = 1, title = "Working correlation structure"
)
```

### Feature selection based on QIC, QICu, and BQICu
For measuring the overall performance based on each working correlation structure, a function will be created called `look` that reports the number of models, where

- the number of features selected is less than the number of non-zero coefficients in the generating model (`under`), 
- only the non-zero features from the generating model were selected (`exact`), 
- the number of features selected matches the number of non-zero coefficients in the generating model; however, at least one of the selected features is NOT one of the non-zero effects in the generating model (i.e., `mis`),
- the number of features selected is greated than the number of non-zero coefficients in the generating model (`over`), and
- the number of features selected is greated than the number of non-zero coefficients in the generating model and include all the non-zero effects (`over_inc`).

```{r, echo = FALSE}
# creating a function to generate a look at the simulation results
look <- function(x) {
    under <- 0
    exact <- 0
    mis <- 0
    over <- 0
    over_inc <- 0
    for (k in seq_len(nsims)) {
        under <- under + (length(x[[k]]$vars) < l)
        exact <- exact + identical(x[[k]]$vars, w)
        mis <- mis + (!identical(x[[k]]$vars, w) & (length(x[[k]]$vars) == l))
        over <- over + (length(x[[k]]$vars) > l)
        over_inc <- over_inc + ((length(x[[k]]$vars) > l) & all(w %in% x[[k]]$vars))
    }
    return(
        data.frame(
            under = under, exact = exact,
            mis = mis, over = over,
            over_inc = over_inc
        )
    )
}
```

Using the `look` function, we have the following summary measures from the simulation set, where the models resulting in the minimum QIC, QICu, and BQICu values were selected as the best fitting model for each working correlation structure.

#### QIC
```{r, echo = FALSE}
data.frame(
    work_corr = c("Independence", "Exchangeable", "AR(1)"),
    dplyr::bind_rows(look(res_indp_qic), look(res_cs_qic), look(res_ar1_qic))
)
```

#### QICu
```{r, echo = FALSE}
data.frame(
    work_corr = c("Independence", "Exchangeable", "AR(1)"),
    dplyr::bind_rows(look(res_indp_qicu), look(res_cs_qicu), look(res_ar1_qicu))
)
```

#### BQICu
```{r, echo = FALSE}
data.frame(
    work_corr = c("Independence", "Exchangeable", "AR(1)"),
    dplyr::bind_rows(look(res_indp_bqicu), look(res_cs_bqicu), look(res_ar1_bqicu))
)
```